\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{mathptmx}
\usepackage[aux]{rerunfilecheck}

\newcommand{\ds}{\displaystyle}

\input{../common.tex}

\title{\commonPSTitleZeroTwoFour}
\author{\commonAuthor}
\date{\commonDateZeroTwoFour}

\begin{document}
\maketitle
\thispagestyle{empty}

\noindent
The following problems based on Section~2.4 of the textbook will help
you study.  \emph{You do not need to hand in solutions to these
  problems.}
\begin{enumerate}
\item (Based on 2.4.1--16) %1
  Differentiate the following functions.
  \begin{multicols}{3}
  \begin{enumerate}
  \item %1a
    $\ds \vphantom{\frac{\theta}{\theta}} f(x)=2x^3+\cos x$
  \item %1b
    $\ds \vphantom{\frac{\theta}{\theta}} G(t)=t^2 \cos t$
    % \item %1c $\ds \vphantom{\frac{\theta}{\theta}} e^x(\sin x + \cos x)$
  \item %1d
    $\ds \vphantom{\frac{\theta}{\theta}} 
    \frac{1-\sin\theta}{\tan\theta + \cos\theta}$
  \end{enumerate}
  \end{multicols}
\item (Based on 2.4.21--24) %2
  Find an equation for the tangent line to the curve $y=x\cos x$
  at the point $(\pi,-\pi)$ on the curve.
\item (Based on 2.4.29--30) %3
  Find $\ds \frac{d^2y}{dx^2}$ for $y=x\cos x$
\item %4
  For what values of $x$ does $f(x)=x+\cos x$ have a horizontal
  tangent? 
\item (Based on 2.4.39--50) %5
  Find the following limits.
  \begin{multicols}{4}
  \begin{enumerate}
  \item %5a
    $\ds \lim_{x\to 0} \frac{\sin 2x}{x}$
  \item %5b
    $\ds \lim_{x\to 0} \frac{\sin 2x}{\sin 3x}$
  \item %5c
    $\ds \lim_{t\to 0} \frac{\sin^3 2t}{t^3}$
  \item %5d
    $\ds \lim_{\theta\to 0} \frac{\cos\theta -1}{\tan\theta}$
  \end{enumerate}
  \end{multicols}
\item (Based on 2.4.17--19) %6
  Use the quotient rule and the derivatives of $\cos x$ and $\sin
  x$ to show that $\ds \frac{d}{dx} \sec x = \sec x \tan x$
\item (Based on 2.4.20) %7
  Use the definition of derivative and the basic trig limits to
  show that $\ds \frac{d}{dx} \cos x = -\sin x$
\item (Based on 2.4.38) %8
  An object with weight $W$ is dragged along a floor by a force
  acting along a rope attached to the object.  If the rope makes an
  angle $\theta$ with the floor, then the magnitude of the total force
  acting on the object is
  \begin{equation*}
    F(\theta) = \frac{\mu W}{\mu\sin\theta + \cos\theta}
  \end{equation*}
  where $\mu$ is a number known as the \textit{coefficient of
    friction} between the object and the floor.
  \begin{enumerate}
  \item %8a
    Find the derivative of $F$ with respect to $\theta$.
  \item %8b
    For what value(s) of $\theta$ is $dF/d\theta = 0$?
  \end{enumerate}
\end{enumerate}

\noindent
You may find the following additional exercises from Section~2.4 helpful.
\begin{itemize}
\item[2.4] 
  C-level: 1--16, 21--24, 25--26, 27--30, 33--34, 39--50; \\
  B-level: 17--20, 31, 32, 35--38; \\
  A-level: 51--52, 53--58
\end{itemize}




\end{document}
