%%% MATH110-PS021-Questions.tex --- 
%% 
%% Filename: MATH110-PS021-Questions.tex
%% Description: 
%% Author: U-ORONYA\edwar
%% Maintainer: 
%% Created: Sun Jan 29 21:43:16 2023 (-0600)
%% Version: 
%% Package-Requires: ()
%% Last-Updated: Tue Jan 14 00:23:04 2025 (-0600)
%%           By: Edward Doolittle
%%     Update #: 4
%% URL: 
%% Doc URL: 
%% Keywords: 
%% Compatibility: 
%% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% 
%%% Commentary: 
%% 
%% 
%% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% 
%%% Change Log:
%% 
%% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Copyright (C) 2023 Edward Doolittle
%% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% 
%%% Code:


\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{mathptmx}
\usepackage[aux]{rerunfilecheck}

\newcommand{\ds}{\displaystyle}

\input{../common.tex}

\title{\commonPSTitleZeroTwoOne}
\author{\commonAuthor}
\date{\commonDateZeroTwoOne}

\begin{document}
\maketitle
\thispagestyle{empty}

\noindent
The following problems based on Section~2.1 of the textbook will help
you study.  \emph{You do not need to hand in solutions to these
  problems.}
\begin{enumerate}
\item (Based on 2.1.1--4) %1
  \begin{enumerate}
  \item Find the slope of the tangent line to the parabola
    $\ds y=x^2-2x-3$ at the point $\ds (0,-3)$ on the parabola.
  \item Find an equation for the tangent line.
  \item Graph the parabola and the tangent line on a common screen.
  \end{enumerate}
\item (Based on 2.1.5--8) %2
  Find an equation of the tangent line to the given curve at the given
  point.
  \begin{multicols}{4}
  \begin{enumerate}
  \item $\ds y=\frac{1}{x+1}$, $\ds (0,1)$
  \item $\ds \vphantom{\frac{1}{1}} y=\sqrt{2x-1}$, $\ds (5,3)$
  \item $\ds \vphantom{\frac{1}{1}} y=x^3-4x$, $\ds (-1,3)$
  \item $\ds y=\frac{x^2}{2x-1}$, $\ds (0,0)$
  \end{enumerate}
  \end{multicols}
\item (Based on 2.1.9--10) %3
  \begin{enumerate}
  \item Find the slope of the tangent line to the curve
    $\ds y=10+3x^2-x^3$ at the point where $\ds x=a$ on the curve.
  \item Use the above result to find the equations of the tangent
    lines to the curve at the points $(1,12)$ and $(3,10)$ on the
    curve.
  \item Graph the curve and both tangents on a common screen.
  \end{enumerate}
\item (Based on 2.1.15--16) %4
  The displacement in meters of a particle moving in a straight line
  is given by the equation of motion $\ds s=1/t$, where $t$ is
  measured in seconds.  Find the velocity and the speed of the
  particle at times $t=a$, $t=1$, $t=2$, and $t=3$.
\item (Based on 2.1.20--21) %5
  Sketch the graph of a function $f$ for which $f(0)=1$, $f'(0)=-1$,
  $f'(1)=0$, and $f'(2)=3$.
\item (Based on 2.1.31--36) %6
  Find the derivatives $f'(a)$ of the following functions from first
  principles.
  \begin{multicols}{4}
  \begin{enumerate}
  \item $\ds f(x)=4x^2-x^3 \vphantom{\frac{x^2}{x}}$
  \item $\ds f(t)=t^4-5t \vphantom{\frac{x^2}{x}}$ 
  \item $\ds f(x)=\frac{x^2+1}{x-2}$ 
  \item $\ds f(x)=\sqrt{3x+1} \vphantom{\frac{x^2}{x}}$ 
  \end{enumerate}
  \end{multicols}
%% \item (Based on 2.1.11--12) A particle starts by moving to the
%%   right along a horizontal line; the graph of the position
%%   function is shown.  % FIXME graph
%%   When is the particle moving to the right?  Stationary?  Moving
%%   to the left?  Draw a graph of the velocity function of the
%%   particle.
\item (Based on 2.1.13--14) %7
  If a ball is thrown straight upward into the air with a velocity of
  $5$ m/s, its height (in meters) after $t$ seconds is given by
  $y=5t-4.9t^2$.  Find the velocity when $t=0.5$.
\item (Based on 2.1.37--42) %8
  Each of the following limits represents the derivative of some
  function $f$ at some number $a$.  State such an $f$ and $a$ in each
  case.
  \begin{multicols}{3}
  \begin{enumerate}
  \item $\ds \lim_{h\to 0} \frac{(2+h)^5-32}{h}$
  \item $\ds \lim_{h\to 0} \frac{\sqrt{16+h}-4}{h}$
  %\item $\ds \lim_{h\to 0} \frac{e^h-1}{h}$
  \item $\ds \lim_{t\to \pi/2} \frac{\sin t-1}{t-\pi/2}$
  \end{enumerate}
  \end{multicols}
\item (Based on 2.1.53--56) %9
  The cost of producing $x$ widgets at a widget factory is $C=f(x)$
  dollars.
  \begin{enumerate}
  \item What is the meaning of the derivative $f'(x)$?  What are its
    units?
  \item What does the statement $f'(100)=12$ mean?
  \item Do you think the values of $f'(x)$ will increase or decrease
    for small increasing values of $x$?  For large increasing values
    of $x$?
  \end{enumerate}
\item (Based on 2.1.59--60) %10
  Calculate $f'(0)$ for the function
  \begin{equation*}
    f(x) = \begin{cases}
      \ds x^2 \cos \frac{1}{x} & \mbox{if $x\ne 0$} \\
      \ds 0                    & \mbox{if $x=0$}
    \end{cases}
  \end{equation*}
\end{enumerate}

\noindent
You may find the following additional exercises from Section~2.1 helpful.
\begin{itemize}
\item[2.1]
  C-level: 1--4, 5--8, 9--10, 15--16, 17--18, 20--23, 27--30,
    31--36, 37--42, 43--44, 47--50; \\
  B-level: 11--12, 13--14, 19, 24--26, 45--46, 51--52, 53--56,
    57--58, 61; \\
  A-level: 59--60
\end{itemize}



\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% MATH110-PS021-Questions.tex ends here
