\documentclass{article}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{mathptmx}
\usepackage{fullpage}
\usepackage[aux]{rerunfilecheck}

\newcommand{\ds}{\displaystyle}

\input{../common.tex}

\title{\commonPSTitleZeroOneFive a (ordinary two-sided limits)}
\author{\commonAuthor}
\date{\commonDateZeroOneFive}

\begin{document}
\maketitle
\thispagestyle{empty}

\noindent
The following problems based on Section~1.5 of the textbook will help
you study.  \emph{You do not need to hand in solutions to these
  problems.}
\begin{enumerate}
\item (Based on 1.5.1) Explain in your own words what is meant by the
  equation
  \begin{equation*}
    \lim_{x\to 3} f(x) = 7
  \end{equation*}
  Is it possible for the above statement to be true yet $f(3)=4$?
  Explain. 
\item (Based on 1.5.22,26) Use a table of values and/or a graphing device
  to estimate the following limits:
  \begin{multicols}{2}
  \begin{enumerate}
  \item $\ds \lim_{x\to 0} \frac{\sqrt{x+9}-3}{x}$
  \item $\ds \lim_{x\to 0} \frac{10^x-2^x}{x}$
  \end{enumerate}
  \end{multicols}
\item Estimate the value of the limit
  % Was based on 1.5.35 in Early Transcendentals ... can't find it now
  \begin{equation*}
    \lim_{x\to 0} (1+x)^{1/x}
  \end{equation*}
  to four decimal places.  Do you recognize the number?  Confirm your
  guess by using a graphing device.
\item (Based on 1.5.23) Use a table of values and/or a graphing device
  to estimate the limit $\ds \lim_{x\to 0} \frac{\tan 3x}{\sin x}$.
\item (Based on 1.5.44) Use a table of values to guess the value of
  the limit $\displaystyle\lim_{x\to 0} \frac{\tan x - x}{x^3}$.  Use
  a graphing device to confirm or disconfirm your guess.
\end{enumerate}

\noindent
You may find the following additional exercises from Section~1.5 helpful.
\begin{itemize}
\item[1.5] 
  C-level: 1, 19--22, 23, 26, 35; \\
  B-level: 32--44; \\
  A-level: 49
\end{itemize}



\end{document}

