\documentclass{article}
\usepackage{fullpage}
%\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[aux]{rerunfilecheck}

\input{../common.tex}

\newcommand{\ds}{\displaystyle}

\title{\commonPSTitleZeroOneFive a\ Solutions}
\author{\commonAuthor}
\date{\commonDateZeroOneFive}

\begin{document}
\maketitle
\begin{enumerate}
\item %1
  Applying the definition, the given equation means ``$f(x)$ can be
  made arbitrarily close to $7$ by making $x$ close to (but not equal
  to) $3$.''  It is possible for
  \begin{equation*}
    \lim_{x\to 3} f(x)=7
  \end{equation*}
  but for $f(3)=4$; for example the function
  \begin{equation*}
    f(x) = \begin{cases}
      x+4 & \mbox{if $x\ne 3$} \\
      4   & \mbox{if $x=3$}
    \end{cases}
  \end{equation*}
  has those properties.
\item %2
  \begin{enumerate}
  \item %2a EJD   
  \item %2b
    We have the following table of values, where $\ds f(x)=\frac{10^x-2^x}{x}$:
    \begin{center}
      \begin{tabular}{|l|r|r|r|}
        \hline
        \multicolumn{1}{|c|}{$x$}   
        & \multicolumn{1}{|c|}{$10^x$}    
	& \multicolumn{1}{|c|}{$2^x$}    
	& \multicolumn{1}{|c|}{$f(x)$}   \\
        \hline\hline
        +1.00   & $10.0000$ & $2.0000$ & $8.0000$ \\
        \hline
        +0.50   &  $3.1623$ & $1.4142$ & $3.4961$ \\
        \hline
        +0.10   &  $1.2589$ & $1.1072$ & $1.8715$ \\
        \hline
        +0.05   &  $1.1220$ & $1.0353$ & $1.7350$ \\
        \hline
        +0.01   &  $1.0233$ & $1.0070$ & $1.6337$ \\
        \hline
        +0.005  &  $1.0116$ & $1.0035$ & $1.6215$ \\
        \hline
        +0.001  &  $1.0023$ & $1.0007$ & $1.6119$ \\
        \hline
        $\pm 0$ &           &          &          \\
        \hline
        -0.001  &  $0.9977$ & $0.9993$ & $1.6070$ \\
        \hline
        -0.005  &  $0.9886$ & $0.9965$ & $1.5974$ \\
        \hline
        -0.01   &  $0.9772$ & $0.9930$ & $1.5855$ \\
        \hline
        -0.05   &  $0.8913$ & $0.9659$ & $1.4937$ \\
      \hline
      \end{tabular}
    \end{center}
    Based on the data, we could reasonably conclude that the limit is
    somewhere between $1.6070$ and $1.6119$.  That may be enough
    accuracy, depending on the use we were going to make of the
    answer.  If not, we could add more lines to the table.  (Methods
    you will learn if you take MATH 111 give $1.609$ as the actual
    answer to three decimal places.)
  \end{enumerate}
\item %3
  We tabulate values of $(1+x)^{1/x}$ for numbers $x$ that are closer
  and closer to $0$ until the values stabilize in the fourth digit.
  We obtain
  \begin{center}
    \begin{tabular}{|l|r|}
      \hline
      \multicolumn{1}{|c|}{$x$}
      & \multicolumn{1}{|c|}{$(1+x)^{1/x}$} \\
      \hline\hline
      +1.0      & 2.00000 \\
      \hline
      +0.1      & 2.59374 \\
      \hline
      +0.01     & 2.70481 \\
      \hline
      +0.001    & 2.71692 \\
      \hline
      +0.0001   & 2.71814 \\
      \hline
      +0.00001  & 2.71826 \\
      \hline 
      +0.000001 & 2.71828 \\
      \hline
    \end{tabular}
  \end{center}
  for small positive values of $x$ and
  \begin{center}
    \begin{tabular}{|l|r|}
      \hline
      \multicolumn{1}{|c|}{$x$}
      & \multicolumn{1}{|c|}{$(1+x)^{1/x}$} \\
      \hline\hline
      $-1.0$     & $\infty$ \\
      \hline
      $-0.1$     & $2.86797$ \\
      \hline
      $-0.01$    & $2.73200$ \\
      \hline
      $-0.001$   & $2.71964$ \\
      \hline
      $-0.0001$  & $2.71841$ \\
      \hline 
      $-0.00001$ & $2.71829$ \\
      \hline
    \end{tabular}
  \end{center}
  for small negative values of $x$.  The two tables agree to four
  digits, so we have (most likely) found the first four digits of the
  limit.  It looks suspiciously like the special number
  $e=2.71828\ldots$ which is the base of the natural exponential and
  logarithmic functions.  We'll see later that the limit is exactly $e$.
\item %4 EJD
  %My graphing device
\item %5
  It's difficult to make an educated guess in this problem.  If you
  follow the instructions in the textbook, you'll see that the limit
  seems to head towards $0.333$, but then as $x$ gets very small, the
  value of $(\tan x -x)/x^3$ suddenly seems to veer down to $0$.  On
  my calculator this happens at about $x=1.0\times 10^{-9}$.

  You should try to use a computer to graph the function at a smaller
  scale than the sample $x$ values given in the textbook to see what
  happens when you really zoom in on the thing.  Something similar
  should happen at a high enough zoom.

  The moral of the story is that adding more accuracy to your inputs
  doesn't necessarily result in more accurate outputs when using the
  numerical approximations provided by calculators and computers.  We
  have to be particularly careful when we subtract two numbers which
  are very close to one another.  You should try to arrange
  calculations so that you don't subtract two numbers which are close,
  if possible.  You can learn more about the associated issues if you
  take a course in numerical methods.

  It is very hard for us to figure out how to evaluate this limit
  given what we now know.  Some of the masters of the art from long
  ago (e.g., Madhava of Sangamagrama) were able to do it, but until
  the development of calculus such calculations were beyond the reach
  of nearly everyone.  If you take MATH 111, you will learn
  straightforward ways to evaluate this limit; L'H\^{o}pital's rule or
  Taylor series tell me that the answer really is $1/3$, so our first
  guess was correct.
\end{enumerate}
\end{document}

