\documentclass{article}
\usepackage{amsmath}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage[aux]{rerunfilecheck}
\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing}

\newcommand{\ds}{\displaystyle}

\input{../common.tex}

\title{\commonPSTitleZeroTwoNine\ Solutions}
\author{\commonAuthor}
\date{\commonDateZeroTwoNine}

\begin{document}
\maketitle
\begin{enumerate}
\item %1
  The best way to remember how to find the linearization is to find
  the equation of the tangent line and then solve for $y$.
  \begin{enumerate}
  \item First note that when $f(a)=f(0)=(2+0)^{-1/2}=1/\sqrt{2}$, so
    $(a,f(a))=(0,1/sqrt{2})$ is the point of interest on the curve.  The slope
    of the tangent line at that point is $f'(a)=(-1/2)(2+a)^{-3/2}=
    (-1/2)(2+0)^{-3/2}=-1/2^{5/2}=-1/(4\sqrt{2})$.  Therefore the equation
    of the tangent line is
    \begin{align*}
      y-\frac{1}{\sqrt{2}} &= -\frac{1}{4\sqrt{2}} (x-0)
    \end{align*}
    Solving for $y$ gives
    \begin{align*}
      y &= \frac{1}{\sqrt{2}} -\frac{1}{4\sqrt{2}} (x-0)
    \end{align*}
    so the linearization of $f(x)$ is
    \begin{align*}
      L(x) &= \frac{1}{\sqrt{2}} -\frac{1}{4\sqrt{2}} x
    \end{align*}
  \item We have $f(a)=16^{3/4}=(16^{1/4})^3=2^3=8$, so $(a,f(a))=(16,8)$
    is the point of interest on the curve.  The slope of the tangent line
    at that point is $f'(a)=(3/4)a^{-1/4} = (3/4) (1/2) = 3/8$ so the
    equation of the tangent line is
    \begin{align*}
      y-8 &= \frac{3}{8} (x-16)
    \end{align*}
    and the linearization of $f(x)$ at $a=16$ is
    \begin{equation*}
      L(x) = 8 + \frac{3}{8} (x-16)
    \end{equation*}
  \end{enumerate}
\item %2
  \begin{enumerate}
  \item By the quotient rule,
    \begin{equation*}
      \frac{dy}{ds} = \frac{(1+2s)-s(2)}{(1+2s)^2}
      = \frac{1}{(1+2s)^2}
    \end{equation*}
    so
    \begin{equation*}
      dy = \frac{1}{(1+2s)^2} ds
    \end{equation*}
    which can also be written
    \begin{equation*}
      dy = \frac{ds}{(1+2s)^2}
    \end{equation*}
  \item Differentiating by the product rule,
    \begin{equation*}
      \frac{dy}{du} = \cos u - u \sin u
    \end{equation*}
    so
    \begin{equation*}
      dy = (\cos u - u\sin u) \; du
    \end{equation*}
    Don't forget the brackets!
  \item Differentiating by the chain rule,
    \begin{equation*}
      \frac{dy}{dt} = 5(t+\tan t)^4 \cdot \frac{d}{dt} (t+\tan t)
      = 5(t+\tan t)^4 (1+\sec^2 t)
    \end{equation*}
    so 
    \begin{equation*}
      dy = 5(t+\tan t)^4 (1+\sec^2 t) \; dt
    \end{equation*}
  \item Differentiating by the chain rule,
    \begin{equation*}
      \frac{dy}{dz} = \frac{1}{2} (z+1/z)^{-1/2} \cdot \frac{d}{dz} (z+1/z)
      = \frac{1}{2} (z+1/z)^{-1/2} \cdot (1-1/z^2)
    \end{equation*}
    so 
    \begin{equation*}
      dy = \frac{1}{2} (z+1/z)^{-1/2} \cdot (1-1/z^2) \cdot dz
    \end{equation*}
  \end{enumerate}
\item \label{prob:dyDeltay} %3
  We have $\Delta y= f(x+\Delta x) - f(x)= \sqrt{1+1} - \sqrt{1}
  = \sqrt{2}-1 \approx 0.4142$, and we have $dy=(1/2) x^{-1/2} \; dx
  = (1/2) 1^{-1/2} \; 1 = 0.5$.  See Figure~\ref{fig:dyDeltay}.
  \begin{figure}[htbp]
    \centering
    \begin{tikzpicture}[scale=2]
      \draw[lightgray,very thin] (0,0) grid (3,2);
      \draw[->] (0,0)--(3,0) node[right] {$x$};
      \draw[->] (0,0)--(0,2) node[above] {$y$};
      \draw[color=red,domain=0:3,smooth,samples=50] plot (\x,{sqrt(\x)}) node[right] {$y=\sqrt{x}$};
      \draw[color=blue,domain=0:3] plot (\x,{0.5*(\x-1)+1}) node[right] {$y=L(x) = \frac{1}{2}(x-1)+1$};
      \draw[color=blue] (1,1)--(2,1)--(2,1.5);
      \node[shape=circle,fill=red,minimum size=3pt,inner sep=1pt] at (1,1) {};
      \draw[color=blue,decorate,decoration={brace,amplitude=3.5pt}] (2,1.5)--(2,1) node[midway,right=1pt] {$dy$};
      \draw[color=red,decorate,decoration={brace,amplitude=3.5pt}] (2,1)--(2,{sqrt(2)}) node[midway,left=1pt] {$\Delta y$};
    \end{tikzpicture}
    \caption{$dy$ versus $\Delta y$ for Problem~\ref{prob:dyDeltay}}
    \label{fig:dyDeltay}
  \end{figure}
\item \label{prob:triangle} %4
  This type of problem is a sort of combination of related rates
  problems and differentials.  It is like a related rates problem in
  that we need to find a relationship between two variables, in this
  case the hypoteneuse and the measured angle; it is different from
  related rates in that time is not a factor.  So instead of
  differentiating with respect to time, we calculate the
  differentials.  (If we wanted to change the problem to be about a
  situation in which $\theta$ were actually changing over time, we
  could put time back into the picture by dividing through by $dt$; do
  that, and compare with what would happen if you had applied the
  operator $d/dt$ to the relationship instead of finding the
  differentials first and dividing by $dt$.)
  \begin{enumerate}
  \item Let $\theta$ be the angle opposite the 20 cm side.  Then
    $\sin\theta = 20/h$; if $\theta$ were exactly $30^{\circ}=\pi/6$
    radians, we would have $\sin\theta = 0.5$ which would mean $h=40$
    cm.  We think of the potential error in measurement as a small
    change in the angle.  We write the small change in the angle as
    $d\theta$, and we try to estimate the resulting change in the
    calculated value of the hypoteneuse $\Delta h \approx dh$.  You
    could figure out $\Delta h$ exactly (try it), but the goal of this
    problem is to estimate it quickly by calculating $dh$ instead.

    Differentiating both sides of the relationship between $\theta$
    and $h$ with respect to $\theta$ gives
    \begin{equation*}
      \cos\theta = -\frac{20}{h^2} \frac{dh}{d\theta}
    \end{equation*}
    by the chain rule.  Multiplying by $d\theta$ gives
    \begin{equation*}
      \cos\theta \; d\theta = -\frac{20}{h^2} \; dh
    \end{equation*}
    When $\theta=30^{\circ}=\pi/6$ and $d\theta=\pm 1^{\circ}\approx\pm 0.0174$ 
    radians
    we have $\cos\theta = \sqrt{3}{2} \approx 0.8660$, $h=40$ (calculated
    above), and so
    \begin{equation*}
      0.8660 \cdot \pm 0.0174 = -\frac{20}{(40)^2} \; dh
      \implies dh \approx \mp 1.209
    \end{equation*}
    So an error of about $1^{\circ}$ smaller in the measured angle
    means that the hypoteneuse is about $1.209$ cm larger than $40$
    cm; an error of about $1^{\circ}$ larger in the measured angle
    means that the hypoteneuse is about $1.209$ cm smaller than $40$
    cm.  See Figure~\ref{fig:triangle}.

    Note that we had to do the calculation in radians; if you did the
    calculation in degrees, you would have gotten the wrong answer!
    \begin{figure}[htbp]
      \centering
      \begin{tikzpicture}[scale=0.1]
        \draw (30:40)--node[midway,right] {$20$} (30:40|-0,0)--(0,0)-- node[midway,sloped,above] {$h$} (30:40);
        \draw[->] (10,0) arc (0:30:10);
        \draw (15:12) node {$\theta$};
      \end{tikzpicture}
      \caption{Triangle for problem~\ref{prob:triangle}}
      \label{fig:triangle}
    \end{figure}
    % FIXME : spruce up the diagram, maybe add some colour, sequence of 3 pics?
    % FIXME : also solution 2, where we solve for $x=20\csc\theta$.
  \item The relative error is $dh/h\approx \mp 1.21/40=0.0302$, so the 
    percentage error is about $\mp 3\%$.
  \end{enumerate}
\end{enumerate}
\end{document}


