\documentclass[12pt]{article}
%\documentclass[12pt,legalpaper]{article}
\usepackage{fullpage}
\usepackage{amsmath,amssymb}
\usepackage{mathptmx}
%\usepackage{fancyheadings}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage[aux]{rerunfilecheck}

%\setlength{\textheight}{11.5in}

\reversemarginpar

\newcommand{\myimp}{\Rightarrow}
\newcommand{\myiff}{\Leftrightarrow}
\newcommand{\mynot}{\neg}
\newcommand{\myor}{\vee}
\newcommand{\myand}{\wedge}
\newcommand{\ds}{\displaystyle}

\DeclareSymbolFont{AMSb}{U}{msb}{m}{n}
\DeclareMathSymbol{\N}{\mathbin}{AMSb}{"4E}
\DeclareMathSymbol{\Z}{\mathbin}{AMSb}{"5A}
\DeclareMathSymbol{\R}{\mathbin}{AMSb}{"52}
\DeclareMathSymbol{\Q}{\mathbin}{AMSb}{"51}
\DeclareMathSymbol{\I}{\mathbin}{AMSb}{"49}
\DeclareMathSymbol{\C}{\mathbin}{AMSb}{"43}

\pagestyle{fancy}
\lhead{MATH 110--003--004 200730                    \\ 
       Midterm Test 2A \hspace{1.25in} Page\ \thepage\ of \pageref{LastPage} \\ 
       Time: 50 minutes                             \\
       \quad}
%\chead{\quad \\ Page\ \thepage\ of \pageref{LastPage} \\ \quad}
\chead{}
\rhead{Name: \underline{\hspace{2in}}        \\ 
       Student \#: \underline{\hspace{2in}}  \\ 
       Section: \underline{\hspace{2in}}     \\
       \quad}
\cfoot{}
\addtolength{\headheight}{\baselineskip}
\addtolength{\headheight}{\baselineskip}
\addtolength{\headheight}{\baselineskip}
\addtolength{\headheight}{\baselineskip}
\renewcommand{\headrulewidth}{0pt}
\fancypagestyle{plain}{%
  \lhead{}
  \chead{UNIVERSITY OF REGINA                \\
    DEPARTMENT OF MATHEMATICS AND STATISTICS \\
    MATH 110--003--004 200730
  }
  \rhead{}
  \cfoot{Page\ \thepage\ of \pageref{LastPage}}
}

\title{Midterm Test 2 (A version)}
\author{Edward Doolittle}

\begin{document}
\thispagestyle{plain}
%\maketitle

\begin{center}
  \quad\\
  \LARGE{Midterm Test 1 (A version)}
\end{center}

\begin{flushleft}
\quad\\
Time: 50 minutes                \hfill       Name: \underline{\hspace{2in}}  \\
Instructors:                    \hfill Student \#: \underline{\hspace{2in}}  \\
\quad Dr. Edward Doolittle      \hfill    Section: \underline{\hspace{2in}}  \\
\end{flushleft}


\noindent
You have 50 minutes to do each of the following questions.
The test is worth a total of 40 marks.
Please\marginpar{\small(marks)} justify your conclusions and
show all your work.
A non-programmable calculator of approved type is permitted.  No other aids
are permitted.
Use the backs of the pages for rough work.

\begin{enumerate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% begin page 1 %%%
\item Find the following derivatives.  Do not simpify!
  \begin{enumerate}
  \item $\ds y'$\marginpar{\small(4)}
    where 
    $\ds y = \tan^2 (3x)$
\vfill
  \item $\ds g''$\marginpar{\small(4)}
    where 
    $\ds g(t)=\sqrt[3]{t^2+1}$
\vfill
  \end{enumerate}
\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% begin page 2 %%%
\item Find\marginpar{\small(4)}
  the differential $dy$ of 
  $\ds y=\frac{s}{1+2s}$
\vfill
\item Find\marginpar{\small(4)} 
  $\ds \lim_{x\to \infty} \left(\sqrt{4x^2+2x}-2x\right)$
\vfill
\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% begin page 3 %%%
\item A\marginpar{\small(6)} rectangular storage container with an open
  top is to have a volume of $10$ m$^3$.  The length of the base must be
  twice
  the width.  Find the dimensions of the container that minimize the
  amount of material used.
  \begin{enumerate}
  \item Sketch a diagram illustrating the situation, labelling important
    quantities with letters.
\vfill
\vfill
  \item Write formulas and for the objective function
    to be minimized and for any constraints.
\vfill
\vfill
  \item Find the minimum value of the objective function.  Use the First
    Derivative Test to ensure that you have a minimum.
\vfill
\vfill
  \item State the solution to the problem in words.
\vfill
  \end{enumerate}
\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% begin page 4 %%%
\item Two\marginpar{\small(5)} 
  cars start moving from the same point.  One travels 
  south at $60$ mi/h
  and the other travels 
  west at $25$ mi/h. 
  At what rate is the distance
  between the cars increasing two hours later?
\vfill
\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% begin page 5 %%%
\item Consider\marginpar{\small(5)}
  the function $f$, given below along with its derivatives.
  \begin{align*}
    f(x) = \frac{2x^2-4x+1}{x^2-2x+4}
    \qquad
    f'(x) = \frac{14(x-1)}{(x^2-2x+4)^2}
    \qquad
    f''(x) = \frac{-42x(x-2)}{(x^2-2x+4)^3}
  \end{align*}
  (Note that the denominators in the above three expressions 
  are always positive.)
  Find each of the following.  \textbf{You do not need to sketch the graph!}
  \begin{enumerate}
  \item The interval(s) on which $f$ is increasing and concave up
\vfill
  \item The interval(s) on which $f$ is increasing and concave down
\vfill
  \item The interval(s) on which $f$ is decreasing and concave up
\vfill
  \item The interval(s) on which $f$ is decreasing and concave down
\vfill
  \item The horizontal asymptote(s) of $f$.
\vfill
  \end{enumerate}
\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% begin page 6 %%%
\item Find\marginpar{\small(4)} 
  $\ds \lim_{\theta\to 0} \frac{\cos\theta - 1}{\tan\theta}$.  
  Do not use L'H\^{o}pital's Rule!
\vfill
\item Show\marginpar{\small(4)} that
  $\ds
    2\sqrt{x} > 3 - \frac{1}{x}
  $
  for all $x>1$.
\vfill
\end{enumerate}

\end{document}
