\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{mathptmx}
\usepackage[aux]{rerunfilecheck}

\newcommand{\ds}{\displaystyle}

\input{../common.tex}

\title{\commonPSTitleZeroThreeFour}
\author{\commonAuthor}
\date{\commonDateZeroThreeFour}


\begin{document}
\maketitle
\thispagestyle{empty}

\noindent
The following problems based on Section~3.4 of the textbook will help
you study.  \emph{You do not need to hand in solutions to these
  problems.}
\begin{enumerate}
\item (Based on 3.4.57--60) %1
  Sketch the graph of a function $f$ that satisfies all of the given
  conditions.
  \begin{multicols}{4}
  \begin{enumerate}
  \item[] $\ds \lim_{x\to -\infty} f(x)=1$
  \item[] $\ds \lim_{x\to \infty} f(x) = -3$
  \item[] $\ds \lim_{x\to 4^-} f(x) = -\infty$
  \item[] $\ds \lim_{x\to 4^+} f(x) = 2$
  \end{enumerate}
  \end{multicols}
\item (Based on 3.4.7--8) %2
  Evaluate the following limit, justifying each step by indicating the
  appropriate properties of limits.
  \begin{equation*}
    \lim_{x\to\infty} \frac{3x^2-8x+2}{x^2+6x-5}
  \end{equation*}
\item (Based on 3.4.9--32) %3
  Find the following limits.
  \begin{multicols}{2}
  \begin{enumerate}
  \item $\ds \lim_{t\to -\infty} \frac{t^2+2}{t^3+t^2-1}$
  \item $\ds \lim_{x\to\infty} \frac{x+2}{\sqrt{9x^2+1}}$
  \item $\ds \lim_{x\to -\infty} \frac{\sqrt{9x^6-x}}{x^3+1}$
  \item $\ds \lim_{x\to -\infty} \left(x+\sqrt{x^2+2x}\right)
    \vphantom{\frac{\sqrt{9x^6}}{x^3}}$
  \end{enumerate}
  \end{multicols}
\item (Based on 3.4.35--40) %4
  Find the horizontal and vertical asymptotes of each of the following
  curves.  Check your work by graphing the curve on a graphing
  calculator or computer and estimating the asymptotes.
  \begin{multicols}{3}
  \begin{enumerate}
  \item $\ds y=\frac{3x-1}{x+2}$
  \item $\ds y=\frac{x^2+x-6}{x^2-3x+2}$
  \item $\ds y=\frac{1+2x^3}{x^3-x}$
  %\item $\ds y=\frac{3e^x-1}{e^x+2}$
  \end{enumerate}
  \end{multicols}
\item (Based on 3.4.6) %5
  Use a graph of the function
  \begin{equation*}
    f(x) = \left(1-\frac{1}{x}\right)^x
  \end{equation*}
  to estimate the value of $\ds \lim_{x\to\infty} f(x)$ to two decimal
  places.  Support your estimate by using a table of values.
% \item (Based on 3.4.33--36) %6
%   Find the following limits.
%   \begin{multicols}{2}
%   \begin{enumerate}
%   %\item $\ds \vphantom{\left(\frac{x^2}{1}\right)} 
%   %  \lim_{x\to\infty} \frac{3e^x+2}{1-5e^x}$
%   %\item $\ds \vphantom{\left(\frac{x^2}{1}\right)} 
%   %  \lim_{x\to -\infty} \frac{3e^x+2}{1-5e^x}$
%   \item $\ds \lim_{x\to \infty} \tan^{-1}\left(\frac{x-1}{x+1}\right)$
%   \item $\ds \lim_{x\to \infty} \tan^{-1}\left(\frac{x-x^2}{x+1}\right)$
%   \end{enumerate}
%   \end{multicols}
\item (Based on 3.4.42) %7
  Calculate the limits
  \begin{equation*}
    \mbox{$\ds \lim_{x\to -\infty} \frac{\sqrt{x^2+1}}{2x-3}$
    \quad and \quad $\ds \lim_{x\to \infty} \frac{\sqrt{x^2+1}}{2x-3}$}
  \end{equation*}
  Check your result by graphing the function.  Can you explain any 
  discrepancy you might notice?
\item (Based on 3.4.45--46) %8
  Find a formula for a function with vertical asymptotes $x=-2$ and
  $x=3$ and horizontal asymptote $y=5/2$.
\item (Based on 3.4.52--56) %9
  Find the limits as $x\to \infty$ and $x\to -\infty$.  Use that
  information, together with intercepts, to give a rough sketch of the
  graph of the function as was done in the textbook.
  \begin{equation*}
    y = f(x) = x^2(x+2)^3(1-x)
  \end{equation*}
\end{enumerate}

\noindent
You may find the following additional exercises from Section~3.4
helpful.
\begin{itemize}
\item[3.4] 
  C-level: 1--40, 44--46, 48--51, 57--60; \\
  B-level: 41--43, 47, 52--56, 61--64; \\
  A-level: 65--74
\end{itemize}

\end{document}

