\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{mathptmx}
\usepackage[aux]{rerunfilecheck}

\input{../common.tex}

\newcommand{\ds}{\displaystyle}

\title{\commonPSTitleZeroZeroB}
\author{\commonAuthor}
\date{\commonDateZeroZeroB}

\begin{document}
\maketitle
\thispagestyle{empty}

\noindent
The following problems based on Appendix~B of the textbook will help
you review.  \emph{You do not need to hand in solutions to these
  problems.}
\begin{enumerate}
\item (Based on B.1--6) Find the distance between the given points.
  \begin{multicols}{4}
  \begin{enumerate}
  \item $\ds (1,2)$, $\ds (4,6)$
  \item $\ds (2,-5)$, $\ds (-3,7)$
  \item $\ds (-1,-3)$, $\ds (-2,6)$
  \item $\ds (b,a)$, $\ds (a,b)$
  \end{enumerate}
  \end{multicols}
\item (Based on B.7--10) Find the slope of the line through $P$ and $Q$.
  \begin{multicols}{3}
  \begin{enumerate}
  \item $\ds P(2,4)$, $\ds Q(5,9)$
  \item $\ds P(-3,5)$, $\ds Q(2,-6)$
  \item $\ds P(-1,0)$, $\ds Q(-3,-7)$
  \end{enumerate}
  \end{multicols}
\item (Based on B.17--18) Sketch the graph of the equation.
  \begin{multicols}{2}
  \begin{enumerate}
  \item $\ds x=2$
  \item $\ds y=-3$
  \end{enumerate}
  \end{multicols}
\item (Based on B.21--36) Find an equation of the line that satisfies the
  given conditions.
  \begin{enumerate}
  \item Through $(-3,1)$, slope $-5/3$
  \item Through $(1,-3)$ and $(-4,-2)$
  \item Slope $2$, $y$-intercept $5$
  \item $x$-intercept $4$, $y$-intercept $-3$
  \item Through $(1,-4)$, parallel to the $x$-axis
  \item Through $(1,-4)$, parallel to the $y$-axis
  \item Through $(2,-3)$, parallel to the line $4x-5y=7$
  \item Through $(-1/2,5/3)$, perpendicular to the line $3x+7y=2$
  \end{enumerate}
\item (Based on B.37--42) Find the slope and $y$-intercept of the line
  and draw its graph.
  \begin{multicols}{4}
  \begin{enumerate}
  \item $\ds x+2y=0$
  \item $\ds 3x-4y=0$
  \item $\ds y=2$
  \item $\ds 3x-2y-5=0$
  \end{enumerate}
  \end{multicols}
\item (Based on B.43--49) Sketch the graph of the region in the $xy$-plane.
  \begin{multicols}{2}
  \begin{enumerate}
  \item $\ds \{(x,y) \, | \, y<0\}$
  \item $\ds \{(x,y) \, | \, \mbox{$x\le 2$ and $y>1$}\}$
  \item $\ds \{(x,y) \, | \, |y|<3\}$
  \item $\ds \{(x,y) \, | \, \mbox{$|x|<4$ and $|y|<3$}\}$
  \end{enumerate}
  \end{multicols}
\item (Based on B.11) Consider the points $A(1,0)$, $B(-2,-3)$, and $C(-3,1)$.
  Show that the distance between $A$ and $C$ is the same as the distance
  between $B$ and $C$.
\item (Based on B.14) 
  \begin{enumerate}
  \item Show that the points $A(-4,7)$, $B(0,-5)$, and $C(2,-11)$ are collinear
    (lie on the same line) by showing that $|AB|+|BC|=|AC|$.
  \item Use slopes to show that $A$, $B$, and $C$ are collinear.
  \end{enumerate}
\item (Based on B.19--20) Sketch the graph of the equation.
  \begin{multicols}{2}
  \begin{enumerate}
  \item $\ds |x|=2$
  \item $\ds xy=0$
  \end{enumerate}
  \end{multicols}
\item (Based on B.50--52) Sketch the region in the $xy$-plane.
  \begin{multicols}{2}
  \begin{enumerate}
  \item $\ds \{(x,y) \, | \, 2y<3x-5\}$
  \item $\ds \{(x,y) \, | \, 3-x<y<3+2x\}$
  \end{enumerate}
  \end{multicols}
\item (Based on B.53) Find a point on the $y$-axis that is equidistant from
  $(4,-3)$ and $(2,5)$.
\end{enumerate}

\noindent
You may find the following additional exercises from Appendix~B helpful.
\begin{itemize}
\item[B] 
  C-level: 1--6, 7--10, 17--18, 21--36, 37--42, 43--44, 46--49; \\
  B-level: 11, 13--16, 19--20, 50--52; \\
  A-level: 12, 45, 53--62
\end{itemize}




\end{document}

