\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{mathptmx}
\usepackage[aux]{rerunfilecheck}

\newcommand{\ds}{\displaystyle}

\input{../common.tex}

\title{\commonPSTitleZeroTwoSix}
\author{\commonAuthor}
\date{\commonDateZeroTwoSix}

\begin{document}
\maketitle
\thispagestyle{empty}

\noindent
The following problems based on Section~2.6 of the textbook will help
you study.  \emph{You do not need to hand in solutions to these
  problems.}
\begin{enumerate}
\item (Based on 2.6.5--20) %1
  Find $dy/dx$ for the following implicitly defined functions.
  \begin{multicols}{3}
  \begin{enumerate}
  \item $\ds x^2+xy-y^2=4$
  \item $\ds \sqrt{x}+2\sqrt{y} = 3$
  %\item $\ds e^{xy} = x+y$
  \item $\ds x^3(x-y) = y^2(x+3y)$
  \end{enumerate}
  \end{multicols}
\item (Based on 2.6.25--30) %2
  Use implicit differentiation to find an equation for the tangent
  line to the given curve at the given point.
  \begin{multicols}{2}
  \begin{enumerate}
  \item $\ds \vphantom{\frac{6}{6}} x^2+xy+y^2=7$; $\ds (1,2)$
  \item $\ds \vphantom{\frac{6}{6}} x^{2/3} + y^{2/3} = \frac{25}{9}$;
    $\ds (-\frac{64}{27},-1)$
  \end{enumerate}
  \end{multicols}
\item (Based on 2.6.31--32) %3
  Use implicit differentiation to find equations for the tangent line
  and normal line for the curve
  \begin{equation*}
    2(x^2+y^2)^2 = 25(x^2-y^2)
  \end{equation*}
  at the point $(3,-1)$.
\item (Based on 2.6.35--38) %4
  Find $y''$ by implicit differentiation for each of the following
  implicitly defined curves.
  \begin{multicols}{2}
  \begin{enumerate}
  \item $\ds 4x^2+9y^2=36$
  \item $\ds x^3+y^3=a^3$
  \end{enumerate}
  \end{multicols}
\item (Based on 2.6.48) %5 FIXME : Trig examples removed from latest edition
  Find the derivatives of the following functions.
  \begin{multicols}{2}
  \begin{enumerate}
  \item $\ds y = \sin^{-1}(\sqrt{x})$
  \item $\ds y = \sqrt{\sin^{-1} x}$
  \item $\ds y = \tan^{-1}(t) + \tan^{-1}(1/t)$
  \item $\ds f(\theta) = \arcsin (2\sin\theta)$
  \end{enumerate}
  \end{multicols}
\item (Based on 2.6.21--22) %6
  If $[f(x)]^2 + x f(x) = 3$ and $f(2) = 1$, find $f'(2)$.
\item (Based on 2.6.23--24) %7
  Regarding $y$ as the independent variable and $x$ as the
  dependent variable, use implicit differentiation to find $dx/dy$ for
  $x^3y^2-xy^3+3xy=0$.
\item (Based on 2.6.44) %8
  Find an equation for the normal line to the ellipse 
  \begin{equation*}
    \frac{x^2}{a^2} + \frac{y^2}{b^2} = 1
  \end{equation*}
  at the point $(x_0,y_0)$ on the ellipse.
\item (Based on 2.6.49--54) %9
  Show that every member of the family of parabolas $x=cy^2$ and
  every member of the family of ellipses $2x^2+y^2=k$ have
  perpendicular tangents where they intersect.
% FIXME : modify this problem
\item (Based on 2.6.60) %10
  Find equations of both tangent lines to 
  \begin{equation*}
    \frac{x^2}{3^2} + \frac{y^2}{6^2} =1 
  \end{equation*}
  which pass through the point $(3,12)$.
\end{enumerate}

\noindent
You may find the following additional exercises from Section~2.6 helpful.
\begin{itemize}
\item[2.6] 
  C-level: 1--4, 5--20, 25--30, 31--32, 33--34, 35--38, 39--40; \\ 
  B-level: 43, 44--45, 46--47; \\
  A-level: 48, 49--52, 53--54, 55, 57--62
\end{itemize}




\end{document}
