\documentclass{article}
\usepackage{amsmath}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage[aux]{rerunfilecheck}
\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing}

\newcommand{\ds}{\displaystyle}

\input{../common.tex}

\title{\commonPSTitleZeroTwoEight\ Solutions}
\author{\commonAuthor}
\date{\commonDateZeroTwoEight}

\begin{document}
\maketitle
\begin{enumerate}
\item %1
  Differentiating both sides of the relationship between $x$ and $y$ with
  respect to time,
  \begin{align*}
    \frac{d}{dt}(x^2+y^2) &= \frac{d}{dt} 25
    \\
    2x\frac{dx}{dt} + 2y\frac{dy}{dt} &= 0
  \end{align*}
  We are given that $dy/dt=6$ and $y=4$, so
  \begin{align*}
    2x\frac{dx}{dt} + 2(4)(6) &= 0
    \\
    \frac{dx}{dt} &= -\frac{24}{x}
  \end{align*}
  To find $dx/dt$, we still need to know $x$.  Fortunately, we can figure
  out $x$ from $y=4$ and the relationship $x^2+y^2=25$: $x^2+16=25$, $x^2=9$,
  $x=\pm 3$, so $dx/dt=\mp 8$.
\item %2
  Differentiating both sides of the given relationship with respect to
  $t$,
  \begin{align*}
    2z\frac{dz}{dt} &= 2x\frac{dx}{dt}+2y\frac{dy}{dt}
  \end{align*}
  Dividing through by $2$ and substituting everything we know,
  \begin{align*}
    z\frac{dz}{dt} &= 5(2) + 12(3) = 46
  \end{align*}
  We still need $z$ in order to figure out $dz/dt$; but from the relationship
  $z^2=x^2+y^2$ and $x=5$ and $y=12$ we have $z^2=5^2+12^2=25+144=169$ so 
  $z=\pm 13$ and so $dz/dt=\pm 46/13$.
\item %3
  The words ``rate'' and ``how fast'' flag this as a related rates
  question.  We need to find a relationship between the non-time variables.
  The volume of a sphere in terms of its radius is $V=(4/3)\pi r^3$.  
  Differentiating the relationship with respect to time we have
  \begin{align*}
    \frac{d}{dt} V &= \frac{d}{dt} \frac{4}{3} \pi r^3 \\
    \frac{dV}{dt} &= \frac{4}{3} \pi \cdot 3r^2 \frac{dr}{dt}
  \end{align*}
  where the chain rule was used in the last step.  The latter expression
  can be simplified to
  \begin{align*}
    \frac{dV}{dt} &= 4\pi r^2 \frac{dr}{dt}
  \end{align*}
  We are given that $dr/dt=4$ and $r=40$ so
  \begin{align*}
    \frac{dV}{dt} &= 4\pi (40)^2 \cdot 4
    \approx 80424
  \end{align*}
  When the radius of the sphere is 40 mm and is increasing at 4 mm/s,
  the volume is increasing at a rate of about 80424 mm$^3$/s.
\item %4 EJD: diagram!
  We need a relationship connecting the surface area $S$
  of a sphere to its diameter $D$.  We have $S=4\pi r^2$ and $r=D/2$ so
  $S=4\pi(D/2)^2=\pi D^2$.  Differentiating with respect to time,
  \begin{equation*}
    \frac{dS}{dt} = 2\pi D \frac{dD}{dt}
  \end{equation*}
  We are given that $dS/dt=-1$ (negative because $S$ is decreasing) 
  and $D=10$, so
  \begin{equation*}
    -1 = 2\pi (10) \frac{dD}{dt}
    \implies
    \frac{dD}{dt} = -\frac{1}{20\pi} \approx -0.0159
  \end{equation*}
  So under the given conditions, the diameter is decreasing at a rate of
  approximately $0.0159$ cm/min.
\item \label{prob:ships} %5
  Call the location of ship B at noon the point $O$.  Call the
  position of ship A with respect to $O$ on the east-west axis through
  $O$ $x(t)$; we are given $x(t)=-150$ when $t=0$ is noon.  Similarly
  call the position of ship B with respect to $O$ on the north-south
  axis through $O$ $y(t)$; we are given $y(t)=0$ when $t=0$ is noon.
  Then at 4 pm, ship A is $150-4(35)=10$ km west of $O$, i.e.,
  $x(4)=-10$, and ship B is $4(25)=100$ km north of $O$, i.e.,
  $y(4)=100$.  Let $z(t)$ be the distance between the two ships at
  time $t$.  By the Pythagorean theorem,
  \begin{align*}
    z^2 &= x^2 + y^2 \\
    z \frac{dz}{dt} &= x\frac{dx}{dt} + y\frac{dy}{dt}
  \end{align*}
  At 4 pm we have $x=-10$, $y=100$, $dx/dt = 35$, $dy/dt=25$ and we can
  calculate $z=\sqrt{10^2+100^2}=\sqrt{10100}\approx 100.5$ (we take the
  positive square root because distances are always positive).  Filling
  in all that information,
  \begin{align*}
    \frac{dz}{dt} &\approx \frac{1}{100.5} (-10\cdot 35 + 100\cdot 25)
    = 21.4
  \end{align*}
  So at 4 pm the distance between the two ships is increasing at a rate
  of 21.4 km/h.  See Figure~\ref{fig:ships}.
  \begin{figure}[htbp]
    \centering
    $\begin{array}{c@{\hspace{0.25in}}c}
    \begin{tikzpicture}[scale=0.02]
      \draw[lightgray,very thin,step=100] (-250,-20) grid (50,150);
      \draw[->] (-250,0)--(50,0) node[right] {$x$};
      \draw[->] (0,-20)--(0,150) node[above] {$y$};
      \node[fill=blue,inner sep=1pt,minimum size=3pt,label=above:$A$] at (-150,0) {};
      \node[fill=red,inner sep=1pt,minimum size=3pt,label=45:$B$] at (0,0) {};
    \end{tikzpicture}
    & 
    \quad
    \begin{tikzpicture}[scale=0.02]
      \draw[lightgray,very thin,step=100] (-250,-20) grid (50,150);
      \draw[->] (-250,0)--(50,0) node[right] {$x$};
      \draw[->] (0,-20)--(0,150) node[above] {$y$};
      \draw (-10,0)--(0,100) node[midway,left] {$z$};
      \node[fill=blue,inner sep=1pt,minimum size=3pt,label=135:$A$] at (-10,0) {};
      \node[fill=red,inner sep=1pt,minimum size=3pt,label=45:$B$] at (0,100) {};
    \end{tikzpicture}
    \\
    \mbox{(a) Situation at noon} & \mbox{(b) Situation at 4pm}
    \end{array}$
    \caption{Diagrams for Problem~\ref{prob:ships}}
    \label{fig:ships}
  \end{figure}
\item %6 EJD: diagram!
  Note: in the problem statement there is a mix of different units (cm and m);
  the easiest way to manage the different units is to convert every meaurement
  into the same system of units.  In this case, we'll convert everything to
  meters.

  The volume of a cone is $V=(1/3)\pi r^2 h$.  The radius and height at the
  top of the cone are $2$ m and $6$ m respectively, so by similar triangles,
  we have $r/h=2/6$ or $r=h/3$.  Substituting into the volume formula,
  $V=(1/3) \pi (h/3)^2 h$ or $V=(\pi/27) h^3$.  Differentiating with respect
  to time,
  \begin{align*}
    \frac{dV}{dt} &= \frac{\pi}{27} \cdot 3h^2 \cdot \frac{dh}{dt} \\
    \frac{dV}{dt} &= \frac{\pi}{9} \cdot h^2 \cdot \frac{dh}{dt}
  \end{align*}
  We are given $h=2$ and $dh/dt=0.2$ (in meters per minute), so
  $dV/dt=(\pi/9) 2^2 \cdot 0.2 \approx 0.2793$ (in cubic meters per minute).
  Since water is running out of the tank at $0.01$ cubic meters per minute,
  the rate at which water is entering the tank must be $0.01+0.2793=0.2893$
  cubic meters per minute.
\item %7
  The formula connecting the variables is $R^{-1}=R_1^{-1}+R_2^{-1}$.
  When $R_1=80$ and $R_2=100$ we have $1/R = 1/80+1/100= 5/400+4/400=9/400$
  so $R=400/9$.  Differentiating the formula with respect to time gives
  \begin{equation*}
    R^{-2} \frac{dR}{dt} = R_1^{-2} \frac{dR_1}{dt} + R_2^{-2} \frac{dR_2}{dt}
  \end{equation*}
  Filling in all the information we know,
  \begin{equation*}
    \frac{9^2}{400^2} \frac{dR}{dt}
    = \frac{1}{80}^2 0.3 + \frac{1}{100^2} 0.2
    \implies 81 \frac{dR}{dt} = 25 \cdot 0.3 + 16 \cdot 0.2
    \implies \frac{dR}{dt} = 0.132
  \end{equation*}
  Under the given conditions $R$ is increasing at a rate of $0.132$ ohms per
  second.
\item %8 EJD: diagram!
  Say the lighthouse is at point $L$.  Then $QPL$ is a right triangle with
  right angle at $P$.  Let $QP=x$ and let the angle $QLP$ be $\theta$.  
  Since $PL=3$ we have $\tan\theta = x/3$ or $x=3\tan\theta$.  Differentiating
  with respect to time, $dx/dt = 3\sec^2\theta \cdot d\theta/dt$.  Since the
  light makes four revolutions per minute, and once complete circle is $2\pi$
  radians, the light circles through an angle of $8\pi$ radians in one minute,
  so $d\theta/dt=8\pi$.  We also have $x=1$ so $\tan\theta = 1/3$.  We could
  figure out $\theta$ from that equation (using the $\tan^{-1}$ button on
  our calculator), but it is easier to note that we really want $\sec^2\theta$.
  From our triangle, the hypoteneuse $QL$ is $\sqrt{1^2+3^2}=\sqrt{10}$ so
  $\cos\theta=3/\sqrt{10}$ so $\sec\theta=\sqrt{10}/3$ so $\sec^2\theta=10/9$.
  Filling that information in to our differential relation,
  \begin{equation*}
    \frac{dx}{dt} = 3\sec^2\theta \cdot \frac{d\theta}{dt}
    = 3 \cdot \frac{10}{9} \cdot 8\pi
    \approx 83.8
  \end{equation*}
  So the light is moving at about 83.8 km per minute at point $Q$ on the 
  shore.
\end{enumerate}
\end{document}


