\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{mathptmx}
\usepackage[aux]{rerunfilecheck}
\usepackage{tikz}
% FIXME : probably don't need these all with circuiTikz
\usetikzlibrary{decorations,decorations.pathmorphing,decorations.pathreplacing}
\usepackage{circuitikz}

\newcommand{\ds}{\displaystyle}

\input{../common.tex}

\title{\commonPSTitleZeroTwoEight}
\author{\commonAuthor}
\date{\commonDateZeroTwoEight}

\begin{document}
\maketitle
\thispagestyle{empty}

\noindent
The following problems based on Section~2.8 of the textbook will help
you study.  \emph{You do not need to hand in solutions to these
  problems.}
\begin{enumerate}
\item (Based on 2.8.10) %1
  If $x^2+y^2=25$ and $dy/dt=6$, find $dx/dt$ when $y=4$.
\item (Based on 2.8.11) %2
  If $z^2=x^2+y^2$, $dx/dt=2$, and $dy/dt=3$, find
  $dz/dt$ when $x=5$ and $y=12$.
\item (Based on 2.8.6) %3
  The radius of a sphere is increasing at a rate of $4$
  mm/s.  How fast is the volume increasing when the radius is $40$ mm?
\item (Based on 2.8.14) %4
  If a snowball melts so that its surface area
  decreases at a rate of $1$ cm$^2$/min, find the rate at which the
  diameter decreases when the diameter is $10$ cm.
\item (Based on 2.8.16) %5
  At noon, ship $A$ is $150$ km west of ship $B$.
  Ship $A$ is sailing east at $35$ km/h and ship $B$ is sailing north at 
  $25$ km/h.  How fast is the distance between the ships changing at
  4:00 pm?
\item (Based on 2.8.25) %6
  Water is leaking out of an inverted conical tank
  at a rate of $10,000$ cm$^3$/min at the same time that water is being
  pumped into the tank at a constant rate.  The tank has height $6$ m
  and the diameter at the top is $4$ m.  If the water level is rising at
  a rate of $20$ cm/min when the height of the water is $2$ m, find the
  rate at which water is being pumped into the tank.
\item (Based on 2.8.39)\label{prob:circuit} %7
  If two resistors $R_1$ and $R_2$ are connected in parallel, as in
  Figure~\ref{fig:circuit}, then the total resistance $R$, measured in
  ohms ($\Omega$), is given by
  \begin{align*}
    \frac{1}{R} = \frac{1}{R_1} + \frac{1}{R_2}
  \end{align*}
  If $R_1$ and $R_2$ are increasing at rates of $0.3$ $\Omega$/s and
  $0.2$ $\Omega$/s respectively, how fast is $R$ changing when
  $R_1=80$ $\Omega$ and $R_2=100$ $\Omega$?
  \begin{figure}[htbp]
    \centering
    \begin{circuitikz}
      \draw (0,0)
      to[V,v=$U_q$] (0,2) % The voltage source
      to[short] (2,2)
      to[R=$R_1$] (2,0) % The resistor
      to[short] (0,0);
      \draw (2,2)
      to[short] (4,2)
      to[R=$R_2$] (4,0)
      to[short] (2,0);
    \end{circuitikz}
    \caption{Electrical circuit for problem~\ref{prob:circuit}}
    \label{fig:circuit}
  \end{figure}
\item (Based on 2.8.44) %8
  A lighthouse is located on a small island $3$ km away from the
  nearest point $P$ on a straight shoreline.  The light in the
  lighthouse makes four revolutions per minute.  How fast is the beam
  of light moving along the shoreline when it is shining on a point
  $Q$ on the shoreline which is $1$ km from $P$?
\end{enumerate}

\noindent
You may find the following additional exercises from Section~2.8  helpful.
\begin{itemize}
\item[2.8] C-level: 1--35; \\
  B-level: 36--40; \\
  A-level: 41--50
\end{itemize}




\end{document}
