%\documentclass{article}
%\usepackage{beamerarticle}
\documentclass[serif,ignorenonframetext]{beamer}

\input{../common.tex}

\usepackage{mathptmx}
\usepackage{multirow}

\newcommand{\ds}{\displaystyle}

\mode<article>{}
\mode<presentation>{\usetheme{\commonTheme}\usecolortheme{\commonColorTheme}}

\title{\commonTitleZeroTwoNine}
\subtitle{\commonSubtitleZeroTwoNine}
\author{\commonAuthor}
\institute{\commonInstitute}
\date{\commonDateZeroTwoNine}

\begin{document}

%\section*{Outline}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}
  \frametitle{Contents}
  \tableofcontents
\end{frame}

\section{Linear Approximations and Differentials}


\subsection{Linear Approximations}

\begin{frame}
  \frametitle{Linear Approximations}
  \begin{itemize}[<+->]
  \item Recall that the big idea of differential calculus is that
    the tangent line is the ``best linear approximation'' to a curve.
  \item The equation of the tangent line in point-slope form
    is $y-f(a)=f'(a)(x-a)$.
  \item Solving for $y$, we have $y=f(a) + f'(a) (x-a)$.
  \item To say that the tangent line is an approximation to the curve
    means $f(x) \approx f(a) + f'(a) (x-a)$.
  \item The function on the right side of the above expressions is
    called the \textbf{linearization} of $f$ at $a$ and is sometimes
    denoted $L(x)$.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Example: $f(x)=\sqrt{25-x^2}$ near $3$}
  \begin{itemize}[<+->]
  \item Let's find the best linear approximation to $f(x)=\sqrt{25-x^2}$
    near $x=3$.
  \item We need to compute $f(3)$ and $f'(3)$.
  \item $\ds f(3)=\sqrt{25-3^2} = \sqrt{16} = 4$.
  \item $\ds f'(x) = \frac{1}{2} (25-x^2)^{-1/2} \cdot -2x$ by the chain
    rule.
  \item $\ds f'(3)= \frac{1}{2} \frac{1}{4} \cdot -6 = -\frac{3}{4}$.
  \item So the linearization of $f(x)$ near $x=3$ is 
    \begin{align*}
      L(x)= f(3) + f'(3) (x-3) = 4 - \frac{3}{4} (x-3)
    \end{align*}
  \item So we can say $\ds \sqrt{25-x^2} \approx 4-\frac{3}{4} (x-3)$.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{The Error in a Linear Approximation}
  \begin{itemize}[<+->]
  \item The approximation $\ds \sqrt{25-x^2} \approx 4-\frac{3}{4} (x-3)$ is
    exact at $x=3$.
  \item The further from $x=3$ we get, the worse the approximation.
  \item The error is exactly $\ds 4-\frac{3}{4} (x-3)-\sqrt{25-x^2}$.
  \item If we knew the error exactly we could figure out $\sqrt{25-x^2}$
    exactly and we wouldn't need an approximation!
  \item So the game now is to estimate the error.
  \item You will study the problem of estimating the error when you study
    Taylor series, beginning in MATH 111.
  \item For now, we will just make some educated guesses.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Range of Applicability of a Linear Approximation}
  \begin{itemize}[<+->]
  \item We will actually turn the problem around.  We will not ask
    for the error or a bound on the error.
  \item Instead we will ask, ``For what $x$ values is the approximation
    $f(x) \approx f(a) + f'(a)(x-a)$ within an error of $0.1$?''
  \item We can translate that statement to an inequality to be solved
    for $x$:
    \begin{align*}
      \left(f(a) + f'(a)(x-a)\right) - 0.1 
      < f(x) 
      < \left(f(a) + f'(a)(x-a)\right) + 0.1
    \end{align*}
  \item For now, the best way for us to solve that inequality is
    graphically.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Applications of Linear Approximations}
  \begin{itemize}[<+->]
  \item Let's find the best linear approximations to $\sin x$ and
    $\cos x$ near $x=0$.
  \item We have $\sin(0)=0$, $\sin'(0)=1$, $\cos(0)=1$, $\cos'(0)=0$.
  \item The best linear approximations are then
    \begin{align*}
      \sin x &\approx \sin(0) + \sin'(0) (x-0) = 0 + 1(x-0) = x \\
      \cos x &\approx \cos(0) + \cos'(0) (x-0) = 1 + 0(x-0) = 1
    \end{align*}
  \item Those approximations are commonly used in physics.
  \item For example, gravitational force on a pendulum is $-mg \sin x$,
    but for small $x$ the approximation $-mg x$ is much easier to work
    with.
  \item In optics, $\sin x \approx x$
    and $\cos x \approx 1$ are used to make lens grinding much easier.
    Those approximations lead to lenses with spherical surfaces, 
    which are very easy to manufacture and work reasonably well
    near the center of the field of vision.
  \end{itemize}
\end{frame}


\subsection{Differentials}

\begin{frame}
  \frametitle{Differentials}
  \begin{itemize}[<+->]
  \item We have the approximation $f(x) \approx f(a) + f'(a)(x-a)$.
  \item We can re-write that as $f(x)-f(a) \approx f'(a) (x-a)$.
  \item Writing $\Delta x = x-a$ and $\Delta y = f(x)-f(a)$ we have
    $\Delta y \approx f'(a) \Delta x$.
  \item Because that approximation applies at any value $a$, we often
    write $\Delta y \approx f'(x) \Delta x$ instead.
  \item For small values of $\Delta x$ the approximation
    is as good as we like.
  \item We imagine that there is a value of $\Delta x$ so small that
    the approximation is perfect, or at least good enough that the
    error is of no consequence.
  \item We write $dx$ instead of $\Delta x$ for such small value of
    the change in $x$; we also write $dy$ instead of $\Delta y$.
  \item In that case, we write $dy = f'(x) \; dx$ exactly.
  \item Instead of ``differences'' $\Delta x$ and $\Delta y$ we talk
    of ``differentials'' $dx$ and $dy$.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Measurement Error}
  \begin{itemize}[<+->]
  \item A common application of differentials is to estimating the
    consequences of measurement error.
  \item If we have a function $y=f(x)$ and we get $x$ from a measurement,
    there will be a measurement error in $x$ which we can call $dx$.
  \item Then the error in the calculated value $y$ will be approximately
    $dy=f'(x) \; dx$.
  \item For example, consider a circle.  We measure its radius $r$
    and then calculate its area $A$ using the formula $A=\pi r^2$.
  \item We have the error in the calculated value $A$ is approximately
    $dA = A'(r) \; dr = 2\pi r \; dr$.
  \item Suppose we have $r=3 cm$ with an error of $0.1$ cm or so.
  \item Then we have $A=\pi r^2 = 9\pi$ with an error of
    $dA = 2\pi r \; dr = 0.6 \pi$ or so.
  %\item The error in the volume of a hypersphere is approximately
  %  $r \; dr \; r \; r$.
  \end{itemize}
\end{frame}


\section{Examples and Exercises}

\begin{frame}
  \frametitle{Examples}
  \begin{enumerate}
  \item Find the linear approximation of $f(x)=\sqrt{1-x}$ near $a=0$
    and use it to approximate $\sqrt{0.9}$ and $\sqrt{1.01}$.
  \item For the function $y=2x-x^2$, compute $\Delta y$ and $dy$ for
    $x=2$ and $dx=\Delta x=-0.4$.  Sketch a diagram illustrating $dx$,
    $dy$, and $\Delta y$.
  \item The radius of a circular disk is given as $24$ cm with a maximum
    error in measurement of $0.2$ cm
    \begin{enumerate}
    \item Use differentials to estimate the maximum error in the calculated
      area of the disk.
    \item What is the relative error?  What is the percentage error?
    \end{enumerate}
  \item Use differentials to estimate the amount of paint needed to
    apply a coat of paint $0.05$ cm thick to a hemispherical dome with
    diameter $50$ m.
  \end{enumerate} 
\end{frame}

\begin{frame}
  \frametitle{Exercises}
  Now you should work on Problem Set~2.9.  After you have finished it,
  you should try the following additional exercises from Section~2.9:
  \begin{itemize}
  \item[2.9] C-level: 1--30; \\
    B-level: 31--34; \\
    A-level: 35--42
  \end{itemize}
\end{frame}


\end{document}

