\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{mathptmx}
\usepackage[aux]{rerunfilecheck}

\newcommand{\ds}{\displaystyle}

\input{../common.tex}

\title{\commonPSTitleZeroFourThree\ Solutions}
\author{\commonAuthor}
\date{\commonDateZeroFourThree}

\begin{document}
\maketitle
\begin{enumerate}
\item
  \begin{enumerate}
  \item By the Fundamental Theorem of Calculus I,
    \begin{equation*}
      g'(x) = \frac{d}{dx} \int_1^x (2+t^4)^5 \; dt
      = (2+x^4)^5
    \end{equation*}
  \item By the Fundamental Theorem of Calculus I,
    \begin{equation*}
      h'(r) = \frac{d}{dr} \int_0^r \sqrt{x^2+4} \; dx
      = \sqrt{r^2+4}
    \end{equation*}
  \item We can't apply the Fundamental Theorem of Calculus I directly
    to answer this question.  We first have to modify $G$ so it is in
    the form which allows us to apply FTC-I:
    \begin{equation*}
      G(x) = \int_x^1 \cos\sqrt{t}\; dt
      = -\int_1^x \cos\sqrt{t}\; dt
    \end{equation*}
    by one of the properties of definite integrals.  Then
    \begin{equation*}
      G'(x) = -\frac{d}{dx}\int_1^x \cos\sqrt{t} \; dt
      = -\cos\sqrt{x}
    \end{equation*}
  \end{enumerate}
\item
  \begin{enumerate}
  \item By the Fundamental Theorem of Calculus II we can write
    \begin{equation*}
      \int_0^1 (3+x\sqrt{x}) \; dx
      = \left. \int (3+x\sqrt{x}) \; dx \right|_0^1
    \end{equation*}
    Evaluating the indefinite integral,
    \begin{equation*}
      \int (3+x\sqrt{x}) \; dx
      = \int (3 + x^{3/2} ) \; dx
      = 3x + \frac{2}{5} x^{5/2} + C
    \end{equation*}
    So
    \begin{equation*}
      \left. \int (3+x\sqrt{x}) \; dx \right|_0^1
      = \left. 3x + \frac{2}{5} x^{5/2} \right|_0^1
      = \left( 3(1) + \frac{2}{5} 1^{5/2} \right)
      - \left( 3(0) + \frac{2}{5} 0^{5/2} \right)
      = 3 + \frac{2}{5} = \frac{17}{5}
    \end{equation*}
  \item We have
    \begin{equation*}
      \int_0^{\pi/4} \sec\theta \tan\theta \; d\theta
      = \left. \int \sec\theta \tan\theta \; d\theta \right|_0^{\pi/4}
      = \left. \vphantom{\int} \sec\theta \right|_0^{\pi/4}
      = \sec\frac{\pi}{4} - \sec{0} = \sqrt{2} - 1
    \end{equation*}
  \item We have
    \begin{equation*}
      \int_1^2 \frac{s^4+1}{s^2} \; ds
      = \left. \int \frac{s^4+1}{s^2} \; ds \right|_1^2
      = \left. \int \left(s^2 + s^{-2}\right) \; ds \right|_1^2
      = \left. \frac{1}{3} s^3 - s^{-1} \right|_1^2
      = \frac{1}{3}2^3 - 2^{-1} - \frac{1}{3}1^3 + 1^{-1}
      = \frac{17}{6}
    \end{equation*}
  \end{enumerate}
\item The integrand is given in cases so we split the definite
  integral at the case boundaries:
  \begin{equation*}
    \int_{-2}^2 f(x) \; dx = \int_{-2}^0 f(x) \; dx + \int_0^2 f(x) \;
    dx
    = \int_{-2}^0 2 \; dx + \int_0^2 (4-x^2) \; dx
  \end{equation*}
  The first integral is
  \begin{equation*}
    \int_{-2}^0 2 \; dx = \left. \int 2 \; dx \right|_{-2}^0
    = \left. \vphantom{\int} 2x \right|_{-2}^0 = 2(0) - 2(-2) = 4
  \end{equation*}
  The second integral is
  \begin{equation*}
    \int_0^2 (4-x^2) \; dx
    = \left. \int (4-x^2) \; dx \right|_0^2
    = \left. \vphantom{\int} 4x - \frac{1}{3} x^3 \right|_0^2
    = 4(2) - \frac{1}{3} 2^3 = 8 - \frac{8}{3} = \frac{16}{3}
  \end{equation*}
  Altogether
  \begin{equation*}
    \int_{-2}^2 f(x) \; dx = \int_{-2}^0 f(x) \; dx + \int_0^2 f(x) \;
    dx
    = \int_{-2}^0 2 \; dx + \int_0^2 (4-x^2) \; dx = 4 + \frac{16}{3}
    = \frac{28}{3}
  \end{equation*}
\item In both cases we are integrating over infinite discontinuities,
  which is not allowed for the Riemann integral.
  \begin{enumerate}
  \item The integrand $4/x^3$ has an infinite discontinuity at $x=0$,
    so any integral of $4/x^3$ over an interval which includes $x=0$,
    e.g., the interval $[-1,2]$, is not well-defined, and the
    Fundamental Theorem of Calculus does not apply.
  \item The integrand $\sec^2 x$ has an infinite discontinuity at
    $x=\pi/2$ because $\sec (\pi/2) = 1/\cos(\pi/2) = 1/0$.  As in the
    previous question, the Riemann integral over the interval
    $[0,\pi]$ is not well-defined, and the Fundamental Theorem of
    Calculus does not apply.
  \end{enumerate}
  In general, before you can apply the Fundamental Theorem of
  Calculus, you should check that the integrand does not have an
  infinite discontinuity in the domain of integration.  If it does,
  you can't apply the Fundamental Theorem of Calculus; you have to use
  more advanced alternative methods, which we will not cover in this
  course.
\item In this case $\Delta x = 1/n$, $x_i = i/n$, the interval is from
  $0$ to $1$, and the integrand is $\sqrt{x}$.  Checking, the
  definition of the integral for $\sqrt{x}$ is
  \begin{equation*}
    \int_0^1 \sqrt{x} \; dx = \lim_{n\to\infty} \sum_{i=1}^n
    \sqrt{x_i} \; \Delta x
    = \lim_{n\to\infty} \left( \sqrt{\frac{1}{n}} + \sqrt{\frac{2}{n}}
      + \cdot + \sqrt{\frac{n}{n}} \right) \cdot \frac{1}{n}
  \end{equation*}
  In this case the integral is easier to evaluate than the limit, so
  we conclude
  \begin{equation*}
    \lim_{n\to\infty} \left( \sqrt{\frac{1}{n}} + \sqrt{\frac{2}{n}}
      + \cdot + \sqrt{\frac{n}{n}} \right) \cdot \frac{1}{n}
    = \int_0^1 \sqrt{x} \; dx = \left. \vphantom{\int} \frac{2}{3}
      x^{3/2} \right|_0^1 = \frac{2}{3}
  \end{equation*}
  which is much easier than trying to evaluate the limit directly.
\end{enumerate}
\end{document}
