\documentclass{article}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{mathptmx}
\usepackage{fullpage}
\usepackage[aux]{rerunfilecheck}

\newcommand{\ds}{\displaystyle}

\input{../common.tex}

\title{\commonPSTitleZeroOneFive b (one-sided and infinite limits)}
\author{\commonAuthor}
\date{\commonDateZeroOneFive}

\begin{document}
\maketitle
\thispagestyle{empty}

\noindent
The following problems based on Section~1.5 of the textbook will help
you study.  \emph{You do not need to hand in solutions to these
  problems.}
\begin{enumerate}
\item (Based on 1.5.2) %1
  Explain what it means to say that
  \begin{equation*}
    \mbox{$\ds \lim_{x\to 2^-} f(x) = 3$ and $\ds \lim_{x\to 2^+} f(x) = 5$}
  \end{equation*}
  In this situation, is it possible for $\ds \lim_{x\to 2} f(x)$ to
  exist?  Explain.  
\item (Based on 1.5.3) %2
  Explain what it means to say that 
  \begin{equation*}
    \lim_{x\to -1} f(x) = -\infty
  \end{equation*}
\item (Based on 1.5.11) %3
  Sketch the graph of the function
  \begin{equation*}
    f(x) = \begin{cases}
      1-x   & \mbox{if $x<-2$} \\
      2x    & \mbox{if $-2\le x < 1$} \\
      3-x^2 & \mbox{if $1\le x$}
    \end{cases}
  \end{equation*}
  and use the graph to determine the values of $a$ for which $\ds
  \lim_{x\to a} f(x)$ exists.
\item (Based on 1.5.15--18) %4
  Sketch the graph of an example of a function $f$ that satisfies
  all of the given conditions.
  \begin{gather*}
    \lim_{x\to 0^-} f(x) = 1
    \qquad
    \lim_{x\to 0^+} f(x) = -1
    \qquad
    \lim_{x\to 2^-} f(x) = 0
    \\
    \lim_{x\to 2^+} f(x) = 1
    \qquad
    f(2) = 1
    \qquad
    \mbox{$f(0)$ is undefined}
  \end{gather*}
\item (Based on 1.5.19) %5
  Guess (to four decimal places) the value of the limit (if it exists)
  \begin{equation*}
    \lim_{x\to 1} \frac{x^2-x}{x^2+x-2}
  \end{equation*}
  by evaluating the function at the numbers $x=2$, $1.1$, $1.01$,
  $1.001$ and at the numbers $x=0$, $0.9$, $0.99$, $0.999$.
\item (Based on 1.5.20) %6
  Guess (to four decimal places) the value of the limit (if it exists)
  \begin{equation*}
    \lim_{x\to -2} \frac{x^2-x}{x^2+x-2}
  \end{equation*}
  by evaluating the function at the numbers $x=-3$, $-2.1$, $-2.01$,
  $-2.001$ and at the numbers $x=-1$, $-1.9$, $-1.99$, $-1.999$.
\item (Based on 1.5.29--39) %7
  Determine the following infinite limits.
  \begin{multicols}{4}
  \begin{enumerate}
  \item $\ds\lim_{x\to -3^-} \frac{x+2}{x+3}$
  \item $\ds\lim_{x\to 0}   \frac{x-1}{x^2(x+2)}$
  \item $\ds\lim_{x\to\pi^-} \cot x\vphantom{\frac{1}{1}}$
  \item $\ds\lim_{x\to 2^-}  \frac{x^2-2x}{x^2-4x+4}$
  \end{enumerate}
  \end{multicols}
\item (Based on 1.5.40) %8
  Find the vertical asymptotes of the function
  $\ds y = \frac{x^2+4}{2x-3x^2}$.
\item (Based on 1.5.47) %9
  Use a graph to estimate the equations of all the vertical asymptotes
  of the curve
  \begin{equation*}
    \mbox{$\ds y = \tan (2\cos x)$, $\ds -\pi\le x \le \pi$}
  \end{equation*}
  Then find the exact equations of the asymptotes using your knowledge
  of the trigonometric functions.
\end{enumerate}

\noindent
You may find the following additional exercises from Section~1.5 helpful.
\begin{itemize}
\item[1.5] C-level: 2--3, 4--5, 7, 8--9, 10, 11--12, 15--18, 24--25,
  29--34, 38--39, 40; \\
  B-level: 6, 11, 13--14, 35--37, 41, 46; \\
  A-level: 47--48
\end{itemize}



\end{document}

