%\documentclass{article}
%\usepackage{beamerarticle}
\documentclass[serif,ignorenonframetext]{beamer}

\input{../common.tex}

\usepackage{mathptmx}
\usepackage{multirow}

\newcommand{\ds}{\displaystyle}

\mode<article>{}
\mode<presentation>{\usetheme{\commonTheme}\usecolortheme{\commonColorTheme}}

\title{\commonTitleZeroTwoSeven}
\subtitle{\commonSubtitleZeroTwoSeven}
\author{\commonAuthor}
\institute{\commonInstitute}
\date{\commonDateZeroTwoSeven}

\begin{document}

%\section*{Outline}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}
  \frametitle{Contents}
  \tableofcontents
\end{frame}


\section{Rates of Change in the Natural and Social Sciences}

\begin{frame}
  \frametitle{Rates of Change}
  \begin{itemize}[<+->]
  \item Recall the concept of average rate of change.
  \item If a variable $y$ depends on a variable $x$, then as $x$ goes
    from $x_1$ to $x_2$, $y$ will go from $y_1$ to $y_2$.
  \item The change in $x$ is $\Delta x = x_2-x_1$.  The corresponding
    change in $y$ is $\Delta y = y_2-y_1$.
  \item The average rate of change is $\ds \frac{\Delta y}{\Delta x}$.
  \item However, it turns out that in many applications an easier concept to 
    work with is the instantaneous rate of change
    $\ds \frac{dy}{dx} = \lim_{\Delta x\to 0} \frac{\Delta y}{\Delta x}$.
  \item We will explore applications of these ideas in physics, chemistry,
    biology, and (micro-)economics.
  \end{itemize}
\end{frame}


\subsection{Physics}

\begin{frame}
  \frametitle{Rates of Change in Physics}
  \begin{itemize}[<+->]
  \item The derivative concept is common in many physical applications.
  \item There are often different names associated with derivatives of
    different quantities in physics.
  \item For example, the derivative of position with respect to time
    is velocity; the derivative of velocity with respect to time
    is acceleration.
  \item The derivative of charge with respect to time is 
    called \textbf{current}.
  \item The derivative of charge with respect to position is \textbf{charge
    gradient}.
  \item The derivative of work with respect to time is \textbf{power}.
  \item The derivative of the amount of radioactive substance is called
    item the \textbf{rate of decay}.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Velocity and Acceleration}
  \begin{itemize}[<+->]
  \item We have already encountered a common application of the rate-of-change
    concept to physics: velocity and acceleration.
  \item Time is the independent variable, usually represented by $t$.
    Position along some line is the dependent variable, usually represented
    by $s(t)$ or $x(t)$.
  \item Velocity means instantaneous velocity, the derivative of the position
    function.  Acceleration means instantaneous acceleration, the derivative
    of the velocity function.
  \item We can interpret the velocity and make conclusions
    about the motion.  When the velocity is positive, the position is
    increasing; when the velocity is negative, the position is decreasing,
    and when the velocity is zero, the position is stationary.
  \item We can make similar interpretations for the acceleration.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Velocity and Acceleration}
  \begin{itemize}[<+->]
  \item Suppose, for example, a prticle moves on a line according to a law
    of motion given by $s(t)=t^3-12t^2+36t$.
  \item The velocity of the particle at time $t$ is $s'(t)=3t^2-24t+36$.
  \item The acceleration of the particle at time $t$ is $s''(t)=6t-24$.
  \item The particle is at rest when $s'(t)=0$, i.e., when $3t^2-24t+36=0$.
    \uncover<+->{Solving the quadratic equation we have $t^2-8t+12=0$ which
    implies $t=2$ and $t=6$.}
  \item The particle is moving in the positive direction when $s'(t)>0$, i.e.,
    when $3t^2-24t+36 > 0$.
    \uncover<+->{Solving that inequality, we have $3(t-2)(t-6)>0$, which is
    the case when both factors have the same sign, i.e., when $t<2$ or $t>6$.}
  \item Similarly, we can figure out when the particle is speeding up by
    solving the inequality $s''(t)>0$.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Linear Density}
  \begin{itemize}[<+->]
  \item In the previous example, we differentiated with respect to time
    to get a \textit{rate}.
  \item We can also differentiate with respect to a space variable.
  \item Consider a metal rod manufactured in such a way that the 
    cumulative mass at a given location $x$ on the rod
    is $m(x)=\sqrt{x}$, where $m$ is measured in kg and $x$ is measured
    in meters from the end of the rod.
  \item The mass of material between locations $x_1$ and $x_2$ 
    is $\Delta m = m(x_2)-m(x_1)$.
  \item The density of material between locations $x_1$ and $x_2$ is
    $[m(x_2)-m(x_1)]/(x_2-x_1)=\Delta m/\Delta x$.
  \item The \textit{linear density} of material is the limit as 
    $\Delta x\to 0$, namely $dm/dx$.
  \item In the above example, the linear density is $d\sqrt{x}/dx
    = 1/(2\sqrt{x})$.
  \end{itemize}
\end{frame}


\subsection{Chemistry}

\begin{frame}
  \frametitle{The Rate of a Reaction}
  \begin{itemize}[<+->]
  \item Consider a chemical reation like NaOH + HCl $\to$ NaCl + H$_2$O.
  \item NaOH and HCl are \textit{reactants}, 
    and NaCl and water H$_2$O are \textit{products}.
  \item We measure the amount of NaCl, say, by its
    \textit{concentration} in moles per liter,
    represented by [NaCl].
  \item Chemists are interested in the rate of change of concentration.
  \item Mass conservation tells us that
    \begin{align*}
      \frac{d[\mbox{NaCl}]}{dt} 
      \uncover<+->{= \frac{d[\mbox{H$_2$O}]}{dt} }%
      \uncover<+->{= -\frac{d[\mbox{NaOH}]}{dt} }%
      \uncover<+->{= -\frac{d[\mbox{HCl}]}{dt} }%
    \end{align*}
  \item That derivative is called the \textit{rate of the reaction}.
  \item In a reaction like 2H$_2$ + O$_2$ $\to$ 2H$_2$O, we write
    \begin{align*}
      \frac{1}{2} \frac{d[\mbox{H$_2$O}]}{dt} 
      \uncover{= -\frac{d[\mbox{O$_2$}]}{dt} }%
      \uncover{= -\frac{1}{2} \frac{d[\mbox{H$_2$}]}{dt} }%
    \end{align*}
  \end{itemize}
\end{frame}


\subsection{Biology}

\begin{frame}
  \frametitle{Population Dynamics}
  \begin{itemize}[<+->]
  \item A standard application of calculus to biology is in the study
    of population changes over time, i.e., population dynamics.
  \item We measure the size of a population by counting individuals,
    so the number is really \textit{discrete}.  However, it is
    convenient to use a continuous
    variable for the size of large populations.
  \item The simplest model of population growth is exponential, $P(t)
    = P_0 2^t$.  You will learn about exponential functions in MATH 111.
  \item Typically, we have some relationship between $dP/dt$ and $P$,
    e.g., 
    \begin{align*}
      \frac{dP}{dt} = r_0 \left(1-\frac{P(t)}{P_c}\right) P(t)-\beta P(t)
    \end{align*}
    and we have to determine something about $P(t)$, e.g., when is $P(t)$
    constant.
  \end{itemize}
\end{frame}


\subsection{Economics}

\begin{frame}
  \frametitle{Marginal Cost}
  \begin{itemize}[<+->]
  \item Suppose we need to produce a widget.  
  \item Producing one widget is very expensive because we have to retool
    our factory.
  \item However, producing \textbf{one more} widget after producing 100
    widgets is probably much less expensive.
  \item The cost of producing one more widget after producing $x$ units
    is called \textbf{the marginal cost at production level $x$.}
  \item The formula for marginal cost is $C(x+1)-C(x)$, where $x$ is the
    production level and $C(x)$ is the cost for an entire production run
    of $x$ units.  For example, the marginal cost of producing one more 
    unit after you have produced 100 units is $C(101)-C(100)$.
  \item The word \textit{marginal} comes from the practice of keeping track
    of the differences $C(x+1)-C(x)$ in the margin of an account.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Marginal Cost and Derivatives}
  \begin{itemize}[<+->]
  \item Marginal cost can be approximated well using derivatives.
  \item Recall that $\ds C'(x) = \lim_{h\to 0} \frac{C(x+h)-C(x)}{h}$.
  \item Since $h=1$ is close to $0$ in a typical economics 
    application, we have
    $\ds C'(x) \approx \frac{C(x+1)-C(x)}{1} = C(x+1)-C(x)$.
  \item In other words, the marginal cost at production level $x$ 
    is usually close enough to $C'(x)$ for the latter to be a useful
    approximation.
  \item Suppose, for example, that the cost of producing $x$ cases 
    of cigars is $C(x)=1000+30x-0.1x^2$.  The $1000$ is the fixed
    start-up cost; the 30 in $20x$ is the cost of materials per unit,
    and the term $-0.1x^2$ is a correction factor for economy of scale.
  \item The marginal cost at production level $50$ is approximately
    $C'(50)=30-0.2(50)=20$.
  \end{itemize}
\end{frame}


\section{Examples and Exercises}

\begin{frame}
  \frametitle{Examples}
  \begin{enumerate}
  \item A particle moves along a horizontal line so that its coordinate
    at time $t$ is $x=\sqrt{b^2+c^2t^2}$, $t \ge 0$, where $b$ and $c$
    are positive constants.
    \begin{enumerate}
    \item Find the velocity and acceleration functions.
    \item Show that the particle always moves in a positive direction.
    \end{enumerate}
  \item The mass of part of a wire is $x(1+\sqrt{x})$ kilograms, where
    $x$ is measured in meters from one end of the wire.  Find the linear
    density of the wire when $x=4$ m.
  \item The cost, in dollars, of producing $x$ units of a certain commodity
    is $\ds C(x)=920+2x-0.02x^2 + 0.00007x^3$.
    \begin{enumerate}
    \item Find the marginal cost function.
    \item Find $C'(100)$ and explain its meaning.
    \item Compare $C'(100)$ with the cost of producing the 101st item.
    \end{enumerate}
  \end{enumerate}
\end{frame}

\begin{frame}
  \frametitle{Exercises}
  Now you should work on Problem Set~2.7.  After you have finished it,
  you should try the following additional exercises from Section~2.7:
  \begin{itemize}
  \item[2.7] C-level: 1--4, 6--10, 17--18, 22, 27--30; \\
    B-level: 11--16, 19--21, 23--24, 25--26; \\
    A-level: 31--36
  \end{itemize}
\end{frame}


\end{document}

