\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{mathptmx}
\usepackage[aux]{rerunfilecheck}

\newcommand{\ds}{\displaystyle}

\input{../common.tex}

\title{\commonPSTitleZeroFourFive}
\author{\commonAuthor}
\date{\commonDateZeroFourFive}

\begin{document}
\maketitle
\thispagestyle{empty}

\noindent
The following problems based on Section~4.5 of the textbook will help
you study.  \emph{You do not need to hand in solutions to these
  problems.}
\begin{enumerate}
\item (Based on 4.5.7--14) %1
  Evaluate the following indefinite integrals using an appropriate
  substitution.
  \begin{multicols}{4}
  \begin{enumerate}
  \item $\ds \int x^2(x^3+5)^9 \; dx
    \vphantom{\frac{x}{\sqrt{x}}}$
  \item $\ds \int (3t+2)^{2.4} \; dt
    \vphantom{\frac{x}{\sqrt{x}}}$
  \item $\ds \int \frac{x}{(x^2+1)^2} \; dx
    \vphantom{\frac{x}{\sqrt{x}}}$
  \item $\ds \int \frac{1}{(5t+4)^{2.7}} \; dt
    \vphantom{\frac{x}{\sqrt{x}}}$
  \end{enumerate}
  \end{multicols}
\item (Based on 4.5.15--22) %2
  Evaluate the following indefinite integrals using an appropriate
  substitution.
  \begin{multicols}{4}
  \begin{enumerate}
  \item $\ds \int \sec 2\theta \tan 2\theta \; d\theta
    \vphantom{\frac{x}{\sqrt{x}}}$
  \item \mbox{$\ds \int \sqrt{x} \; \sin(1+x^{3/2}) \; dx
    \vphantom{\frac{x}{\sqrt{x}}}$}
  \item $\ds \int \frac{\cos(\pi/x)}{x^2} \; dx
    \vphantom{\frac{x}{\sqrt{x}}}$
  \item \mbox{$\ds \int (1+\tan\theta)^5 \sec^2\theta \; d\theta
    \vphantom{\frac{x}{\sqrt{x}}}$}
  \end{enumerate}
  \end{multicols}
\item (Based on 4.5.23--30) %3
  Evaluate the following indefinite integrals using an appropriate
  substitution.
  \begin{multicols}{4}
  \begin{enumerate}
  \item $\ds \int \frac{dt}{\cos^2 t\sqrt{1+\tan t}}
    \vphantom{\frac{x}{\sqrt{x}}}$
  \item $\ds \int \sin t \; \sec^2(\cos t) \; dt
    \vphantom{\frac{x}{\sqrt{x}}}$
  \item $\ds \int \frac{x^2}{\sqrt{1-x}} \; dx
    \vphantom{\frac{x}{\sqrt{x}}}$
  \item $\ds \int x^3 \sqrt{x^2+1} \; dx
    \vphantom{\frac{x}{\sqrt{x}}}$
  \end{enumerate}
  \end{multicols}
\item (Based on 4.5.35--51) %4
  Evaluate the following definite integrals using an appropriate
  substitution.
  \begin{multicols}{4}
  \begin{enumerate}
  \item $\ds \int_0^{\pi/2} \cos x \; \sin(\sin x) \; dx
    \vphantom{\frac{x}{\sqrt{x}}}$
  \item $\ds \int_0^a x \sqrt{a^2-x^2} \; dx
    \vphantom{\frac{x}{\sqrt{x}}}$
  \item $\ds \int_0^4 \frac{x}{\sqrt{1+2x}} \; dx
    \vphantom{\frac{x}{\sqrt{x}}}$
  \item \mbox{$\ds \int_0^{T/2} \sin(2\pi t/T-\alpha) \; dt
    \vphantom{\frac{x}{\sqrt{x}}}$}
  \end{enumerate}
  \end{multicols}
\item (Based on 4.5.55--56) %5
  \begin{enumerate}
  \item Evaluate $\ds \int_{-2}^2 (x+3) \sqrt{4-x^2} \; dx$ by writing it
    as a sum of two integrals and interpreting one of those integrals in
    terms of an area.
  \item Evaluate $\ds \int_0^1 x\sqrt{1-x^4} \; dx$ by making a substitution
    and interpreting the resulting integral in terms of an area.
  \end{enumerate}
\item Evaluate the following integrals.
  \begin{multicols}{2}
    \begin{enumerate}
    \item $\ds \int \cos^3 x \; \sin^6 x \; dx
      \vphantom{\frac{x}{\sqrt{x}}}$
    \item $\ds \int_{-1}^1 \frac{x^2 \tan x}{x^4+1} \; dx
      \vphantom{\frac{x}{\sqrt{x}}}$
    \end{enumerate}
  \end{multicols}
\item (Based on 4.5.60) %6
  If $f$ is continuous and $\ds \int_0^9 f(x) \; dx = 4$, find
  $\ds \int_0^3 xf(x^2) \; dx$.
\item (Based on 4.5.64) %7
  If $f$ is continuous on $[0,\pi]$, use the substitution $u=\pi-x$ to
  show that
  \begin{align*}
    \int_0^\pi xf(\sin x) \; dx = \frac{\pi}{2} \int_0^\pi f(\sin x) \; dx
  \end{align*}
\end{enumerate}

\noindent
You may find the following additional exercises from Section~4.5
helpful.
\begin{itemize}
\item[4.5]
  C-level: 1--51; \\
  B-level: 52--60; \\
  A-level: 61--66
\end{itemize}

\end{document}



