%\documentclass{article}
%\usepackage{beamerarticle}
\documentclass[serif,ignorenonframetext]{beamer}

\input{../common.tex}

\usepackage{mathptmx}
\usepackage{multirow}

\newcommand{\ds}{\displaystyle}

\mode<article>{}
\mode<presentation>{\usetheme{\commonTheme}\usecolortheme{\commonColorTheme}}

\title{\commonTitleZeroFourTwo}
\subtitle{\commonSubtitleZeroFourTwo}
\author{\commonAuthor}
\institute{\commonInstitute}
\date{\commonDateZeroFourTwo}


\begin{document}

%\section*{Outline}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}
  \frametitle{Contents}
  \tableofcontents
\end{frame}


\section{The Definite Integral}

\subsection{Definite Integrals}

\begin{frame}
  \frametitle{Definition of a Definite Integral}
  \begin{itemize}[<+->]
  % analogy with differentiation
  \item We have seen expressions like $\ds \lim_{n\to\infty} \sum_{i=1}^n
    f(x_i^*) \Delta x$ for areas.
  \item Such expressions show up in other contexts, e.g., calculating
    work done.
    They are so common that they have a special notation.
  \item \textbf{Definition:}  Let $f$ be a function on an interval
    $[a,b]$.  Divide
    the interval into equal subintervals of length $\Delta x=(b-a)/n$
    and let $x_0=a$, $x_1=a+(1/n)(b-a)$, \ldots, $x_n=a+(n/n)(b-a)/n=b$
    be the endpoints of those intervals.  Let $x_i^*$ be any \textbf{sample
    points} in those intervals.  Then the \textbf{definite integral of $f$
    from $a$ to $b$ is}
    \begin{align*}
      \int_a^b f(x) \; dx = \lim_{n\to\infty} \sum_{i=1}^n f(x_i^*) \Delta x
    \end{align*}
    provided that the limit exists.  If it does exist, we say $f$ is
    integrable.
  \end{itemize}
\end{frame}

% EJD: use Tikz to colourize the important parts.
\begin{frame}
  \frame{Notation}
  \begin{itemize}[<+->]
  \item The symbol $\int$ is called an integral sign.
  \item It's an elongated $S$ and stands for the Latin word ``summa'' for
    sum.
  \item In the notation $\int_a^b f(x) \; dx$, $f(x)$ is called the
    \textbf{integrand}.
  \item $a$ and $b$ are called the \textbf{limits of integration}; $a$
    is the \textbf{lower limit} and $b$ is the \textbf{upper limit}.
  \end{itemize}
\end{frame}

% EJD: augment this slide show

\subsection{Evaluating Integrals}

\begin{frame}
  \frametitle{Evaluating Integrals}
  \begin{itemize}[<+->]
  \item EJD
  \end{itemize}
\end{frame}


\subsection{Properties of Integrals}

\begin{frame}
  \frametitle{Properties of Integrals}
  \begin{itemize}[<+->]
  \item EJD
  \end{itemize}
\end{frame}

\section{Examples and Exercises}

\begin{frame}
  \frametitle{Examples}
  \begin{enumerate}
  \item 
    \begin{enumerate}
    \item Evaluate the Riemann sum for $f(x)=x^2-x$, $0\le x\le 2$ with
      four subintervals, taking the sample points to be right endpoints.
      Explain, with the aid of a diagram, what the Riemann sum represents.
    \item Use the definition of a definite integral (with right enpoints)
      to calculate the value of the integral
      $\ds \int_0^2 (x^2-x) \; dx$.
    \end{enumerate}
  \item Evaluate
    $\ds \int_0^1 \left( x+\sqrt{1-x^2}\right) \; dx$
    by interpreting it in terms of areas.
  \item If $\ds \int_0^6 f(x) \; dx = 10$ and
    $\ds \int_0^4 f(x) \; dx = 7$, find $\ds \int_4^6 f(x) \; dx$.
  \end{enumerate} 
\end{frame}

\begin{frame}
  \frametitle{Exercises}
  Now you should work on Problem Set~4.2.  After you have finished it,
  you should try the following additional exercises from Section~4.2:
  \begin{itemize}
  \item[4.2]
    C-level: 1--8, 17--30, 33--51; \\
    B-level: 52--64; \\
    A-level: 65--75
  \end{itemize}
\end{frame}


\end{document}

