\documentclass{article}
\usepackage{amsmath}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage[aux]{rerunfilecheck}

\newcommand{\ds}{\displaystyle}

\input{../common.tex}

\title{\commonPSTitleZeroTwoSeven\ Solutions}
\author{\commonAuthor}
\date{\commonDateZeroTwoSeven}

\begin{document}
\maketitle
\begin{enumerate}
\item %1
  \begin{enumerate}
  \item This question can be answered with or without calculus.
    Without calculus, we can complete the square to obtain
    \begin{align*}
      s &= -16(t^2-5t) 
      = -16\left(t^2-2\frac{5}{2}t
        +\left(\frac{5}{2}\right)^2-\left(\frac{5}{2}\right)^2\right)
      = -16\left(t-\frac{5}{2}\right)^2+16\left(\frac{5}{2}\right)^2
      = -16\left(t-\frac{5}{2}\right)^2+100
    \end{align*}
    which has a maximum value of $100$, so the ball reaches a maximum
    height of $100$ ft.

    With calculus, note that the ball reaches a maximum height when it
    is no longer moving upwards, i.e., when $s'=0$, which occurs when
    $80-32t=0$, i.e., $t=5/2$ seconds.  At that time, the ball is at a
    height of $s(5/2)=80(5/2)-16(5/2)^2=200-100=100$ ft.
  \item When the ball is 96 ft above the ground we have
    $s(t)=80t-16t^2=96$ which gives $16t^2-80t+96=0$, $t^2-5t+6=0$
    $(t-2)(t-3)=0$, so the ball is $96$ ft above the ground when $t=2$
    seconds and when $t=3$ seconds.  Note that the velocity of the
    ball is the derivative of $s$ so $s'(t)=80-32t$; at $t=2$ we have
    $s'(2)=80-32(2)=80-64=16$, so the ball is moving upwards (positive
    is up in this problem) at 16 ft/s.  When $t=3$ we have
    $s'(3)=80-32(3)=80-96=-16$, so the ball is moving downwards at 16
    ft/s.
  \end{enumerate}
\item %2
  Based on the formula for linear density in the textbook, the linear
  density is $m'(x)=6x$ kg/m.  (a) When $x=1$ the linear density is
  $m'(1)=6$ kg/m; (b) 12 kg/m; (c) 18 kg/m.
\item %3
  \begin{enumerate}
  \item We have $C'(x)=25-0.18x+0.0012x^2$ so $C'(100)=25-18+12=19$.
    We interpret this as an approximation to the marginal cost, i.e.,
    the cost of producing one more unit of the commodity after we have
    produced 100 is approximately $19$ monetary units.  (The problem
    doesn't state what those units are; they could be dollars,
    thousands of dollars, millions of dollars, etc.)
  \item The exact cost of producing one more item after 100 have been
    produced is
    \begin{align*}
      M
      &=C(101)-C(100)
      \\
      &= 339+25(101)-0.09(101)^2+0.0004(101)^3
      -(339+25(100)-0.09(100)^2+0.0004(100)^3)
      \\
      &= 19.0304
    \end{align*}
    We can see that the marginal cost is very close to the
    approximation in the previous part; the relative error is
    $0.0304/19=0.0016$, or 0.16\%.
  \end{enumerate}
\item %4
  \begin{enumerate}
  \item The rate of the reaction is 
    \begin{equation*}
      d[C]/dt= \frac{d}{dt} \frac{a^2kt}{akt+1}
      = \frac{(akt+1)(a^2k)-a^2kt(ak)}{(akt+1)^2}
      = \frac{a^3k^2t+a^2k-a^3k^2t}{(akt+1)^2}
      = \frac{a^2k}{(akt+1)^2}
    \end{equation*}
  \item We have worked out the left side of the purported identity
    above.  The right side is
    \begin{equation*}
      k(a-x)^2 = k\left(a-\frac{a^2kt}{akt+1}\right)^2
      = k\left(\frac{a^2kt+a-a^2kt}{akt+1}\right)^2
      = k\frac{a^2}{(akt+1)^2}
    \end{equation*}
    which is the same as the left side and we are done.
  \end{enumerate}
\item %5
  \begin{enumerate}
  \item By a stable population, we mean a population which doesn't
    change in number (of course, the particular individuals will
    change from year to year, but the number of them won't).  That
    means $P$ is constant throughout time, so $dP/dt=0$.
  \item We are given $P_c=10,000$, $r_0=0.05$, and $\beta=0.04$;
    furthermore, if the population is stable, we have $dP/dt=0$.
    Substituting those values into the equation, we have
    \begin{equation*}
      0 = 0.05\left(1-\frac{P(t)}{10,000}\right)P(t)-0.04P(t)
    \end{equation*}
    Clearing fractions by multiplying through by $10,000$ and
    factoring,
    \begin{equation*}
      0 = P(t) (0.05 \left(10,000 - P(t)\right) - 400)
      = P(t) (100 - 0.05P(t))
    \end{equation*}
    with solutions $P(t)=0$ and $P(t)=2000$.  The stable population
    levels are $P(t)=0$ and $P(t)=2000$; if we have no fish, we will
    continue to have no fish; on the other hand, if we have any other
    number of fish, the population will in the long run tend to
    $2,000$ fish, meaning we'll only be able to harvest about 80 fish
    per year in the long run.
  \item As with the previous, we have $P_c=10,000$, $r_0=0.05$, and
    $dP/dt=0$, but now we have $\beta=0.05$ instead of $0.04$, which
    could happen, say, if we tried to harvest $100$ fish per year at
    the $2,000$ population level.  In that case our equation becomes
    \begin{equation*}
      0 = 0.05\left(1-\frac{P(t)}{10,000}\right)P(t)-0.05P(t)
    \end{equation*}
    Clearing fractions by multiplying through by $10,000$ and
    factoring,
    \begin{equation*}
      0 = P(t) (0.05 \left(10,000 - P(t)\right) - 500)
      = P(t) (-0.05P(t))
    \end{equation*}
    with only the solution $P(t)=0$.  That means that no matter how
    many fish we start with, in the long run we'll have no fish under
    those conditions.
  \end{enumerate}
\end{enumerate}
\end{document}


