\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{mathptmx}
\usepackage[aux]{rerunfilecheck}

\newcommand{\ds}{\displaystyle}

\input{../common.tex}

\title{\commonPSTitleZeroTwoSeven}
\author{\commonAuthor}
\date{\commonDateZeroTwoSeven}

\begin{document}
\maketitle
\thispagestyle{empty}

\noindent
The following problems based on Section~2.7 of the textbook will help
you study.  \emph{You do not need to hand in solutions to these
  problems.}
\begin{enumerate}
\item (Based on 2.7.8--9) %1
  If a ball is thrown vertically upward with a velocity of 
  $80$ ft/s, then its height after $t$ seconds is $s=80t-16t^2$.
  \begin{enumerate}
  \item What is the maximum height reached by the ball?
  \item What is the velocity of the ball when it is 96 ft above
    the ground on the way up?  On the way down?
  \end{enumerate}
\item (Based on 2.7.17) %2
  The mass of the part of a metal rod that lies between its left
  end and a point $x$ meters to the right is $3x^2$ kg.  Find the
  linear density when $x$ is (a) 1 m, (b) 2 m, and (c) 3 m.
\item (Based on 2.7.29--30) %3
  The cost function for production of a commodity is
  $C(x)=339+25x-0.09x^2+0.0004x^3$.  
  \begin{enumerate}
  \item Find and interpret $C'(100)$
  \item Compare $C'(100)$ with the exact marginal cost at production
    level $100$, i.e., the cost $C(101)-C(100)$ of producing the
    101st item after 100 items have been produced.
  \end{enumerate}
\item (Based on 2.7.24) %4
  Consider the chemical reaction $\mbox{A} + \mbox{B} \to \mbox{C}$ in
  which one molecule of reactant A combines with one molecule of 
  reactant B to form one molecule of product C.  If the initial
  concentrations of A and B are the same, say $a$ moles/L, it turns out
  that the concentration of C as a function of time is given explicitly
  by the formula $[\mbox{C}]=a^2kt/(akt+1)$ where $k$ is a constant
  depending on the type of reaction.
  \begin{enumerate}
  \item Find the rate of reaction at time $t$.
  \item Show that if $x(t)=[\mbox{C}]$ then $dx/dt = k(a-x)^2$.
  \end{enumerate}
\item (Based on 2.7.36) %5
  In a fish farm, a population of fish is introduced into a pond and
  harvested regularly.  A model for the rate of change of the fish
  population is given by the equation
  \begin{align*}
    \frac{dP}{dt} = r_0 \left(1-\frac{P(t)}{P_c}\right) P(t) - \beta P(t)
  \end{align*}
  where $r_0$ is the birth rate of the fish, $P_c$ is the maximum population
  that the pond can sustain (called the \textit{carrying capacity}), and
  $\beta$ is the percentage of the population that is harvested.
  \begin{enumerate}
  \item What value of $dP/dt$ corresponds to a stable population?
  \item If the pond can sustain $10,000$ fish, the birth rate is 5\%,
    and the harvesting rate is 4\%, find the stable population level.
  \item What happens if the harvesting rate $\beta$ is raised to 5\%?
  \end{enumerate}
\end{enumerate}

\noindent
You may find the following additional exercises from Section~2.7 helpful.
\begin{itemize}
\item[2.7] C-level: 1--4, 6--10, 17--18, 22, 27--30; \\
  B-level: 11--16, 19--21, 23--24, 25--26; \\
  A-level: 31--36
\end{itemize}




\end{document}
