\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{mathptmx}
\usepackage[aux]{rerunfilecheck}

\input{../common.tex}

\newcommand{\ds}{\displaystyle}

\title{\commonPSTitleZeroZeroC}
\author{\commonAuthor}
\date{\commonDateZeroZeroC}

\begin{document}
\maketitle
\thispagestyle{empty}

\noindent
The following problems based on Appendix~C of the textbook will help
you review.  \emph{You do not need to hand in solutions to these
  problems.}
\begin{enumerate}
\item (Based on C.1--4) Find an equation of a circle that satisfies the
  given conditions.
  \begin{enumerate}
  \item Center $(4,3)$, radius $5$
  \item Center $(-2,7)$, radius $3$
  \item Center at the origin, passes through $(-5,12)$
  \item Center $(3,-8)$, passes through the origin
  \end{enumerate}
\item (Based on C.5--9) Show that the equation represents a circle, and find
  its center and radius.
  \begin{multicols}{2}
  \begin{enumerate}
  \item $\ds x^2+y^2+2x=0$
  \item $\ds x^2+y^2+10x-6y+8=0$
  \item $\ds x^2+y^2-y=6$
  \item $\ds 3x^2+3y^2+x-2y-5=0$
  \end{enumerate}
  \end{multicols}
\item (Based on C.11--30) Identify the type of curve and sketch the graph.
  Do not plot points.  Just use the standard graphs given in the textbook
  and shift if necessary.
  \begin{multicols}{4}
  \begin{enumerate}
  \item $\ds 9x^2+y^2=1$
  \item $\ds x=y^2+4$
  \item $\ds 16y^2-9x^2=25$
  \item $\ds y^2-x^2+4y=10$
  \end{enumerate}
  \end{multicols}
\item (Based on C.33--34) Sketch the region bounded by the curves.
  \begin{multicols}{2}
  \begin{enumerate}
  \item $\ds y=-x^2$, $y=5x$
  \item $\ds y=x^2-1$, $y=2x+2$
  \end{enumerate}
  \end{multicols}
\item (Based on C.31--32) Identify the type of curve and sketch the graph.
  Do not plot points.  Just use the standard graphs given in the textbook
  and shift if necessary.
  \begin{multicols}{2}
  \begin{enumerate}
  \item $\ds x^2+4y^2-32y=16$
  \item $\ds 9x^2-4y^2-6x+5=0$
  \end{enumerate}
  \end{multicols}
\item (Based on C.35) Find an equation of the parabola with vertex $(1,5)$
  that opens downward and passes through the point $(-1,-4)$.
\item (Based on C.37--40) Sketch the graph of the set.
  \begin{multicols}{2}
  \begin{enumerate}
  \item $\ds \{(x,y)|x^2+y^2\le 4\}$
  \item $\ds \{(x,y)|x^2+y^2>1\}$
  \item $\ds \{(x,y)|y>x^2-2x\}$
  \item $\ds \{(x,y)|16x^2+9y^2\le 25\}$
  \end{enumerate}
  \end{multicols}
\item (Based on C.10) Under what condition on the coefficients $a$, $b$, and
  $c$ does the equation $x^2+4y^2+ax+by+c=0$ represent an ellipse?  When
  that condition is satisfied, find the center of the ellipse.
\end{enumerate}

\noindent
You may find the following additional exercises from Appendix~C helpful.
\begin{itemize}
\item[C] 
  C-level: 1--4, 5--9, 11--30, 33--34; \\
  B-level: 10, 31--32, 35--36, 37--40
\end{itemize}

\end{document}

