\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{mathptmx}
\usepackage[aux]{rerunfilecheck}

\newcommand{\ds}{\displaystyle}

\input{../common.tex}

\title{\commonPSTitleZeroThreeTwo}
\author{\commonAuthor}
\date{\commonDateZeroThreeTwo}

\begin{document}
\maketitle
\thispagestyle{empty}

\noindent
The following problems based on Section~3.2 of the textbook will help
you study.  \emph{You do not need to hand in solutions to these
  problems.}
\begin{enumerate}
\item (Based on 3.2.5--8)
  Verify that the following functions satisfy the three hypotheses of Rolle's
  Theorem on the given interval.  Then find all numbers $c$ that satisfy
  the conclusion of Rolle's Theorem.
  \begin{multicols}{2}
  \begin{enumerate}
  \item $f(x)=x^3-x^2-6x+2$, $[0,3]$
  \item $f(x)=\cos 2x$, $[\pi/8,7\pi/8]$
  \end{enumerate}
  \end{multicols}
\item (Based on 3.2.11--14)
  Verify that the following functions satisfy the hypotheses of the Mean Value
  Theorem on the given interval.  Then find all numbers $c$ which satisfy
  the conclusion of the Mean Value Theorem.
  \begin{multicols}{2}
  \begin{enumerate}
  \item $\ds f(x)=x^3+x-1\vphantom{\frac{x}{x+2}}$, $[0,2]$
  \item $\ds f(x)=\frac{x}{x+2}$, $[1,4]$
  \end{enumerate}
  \end{multicols}
\item (Based on 3.2.9)
  Let $f(x)=1-x^{2/3}$.  Show that $f(-1)=f(1)$ but there is no number
  $c$ in $(-1,1)$ such that $f'(c)=0$.  Why does this not contradict
  Rolle's Theorem?
\item (Based on 3.2.17--18)
  Let $f(x)=(x-3)^{-2}$.  Show that there is no number $c$ in
  $(1,4)$ such that $f(4)-f(1)=f'(c)(4-1)$.  Why does this not 
  contradict the Mean Value Theorem?
\item (Based on 3.2.19--20)
  Show that the equation $2x-1-\sin x=0$ has exactly one real root.
\item (Based on 3.2.31)
  Use the Mean Value Theorem to prove the inequality 
  $|\sin a-\sin b|\le |a-b|$ for all $a$ and $b$.
\end{enumerate}

\noindent
You may find the following additional exercises from Section~3.2
helpful.
\begin{itemize}
\item[3.2] 
  C-level: 1--20, 34; \\
  B-level: 25--27, 29, 33, 35; \\
  A-level: 21--22, 23--24, 28, 30--32, 36
\end{itemize}

\end{document}

