%\documentclass{article}
%\usepackage{beamerarticle}
\documentclass[serif,ignorenonframetext]{beamer}

\input{../common.tex}

\usepackage{mathptmx}
\usepackage{multirow}

\newcommand{\ds}{\displaystyle}

\mode<article>{}
\mode<presentation>{\usetheme{\commonTheme}\usecolortheme{\commonColorTheme}}

\title{\commonTitleZeroThreeOne}
\subtitle{\commonSubtitleZeroThreeOne}
\author{\commonAuthor}
\institute{\commonInstitute}
\date{\commonDateZeroThreeOne}

\begin{document}

%\section*{Outline}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}
  \frametitle{Contents}
  \tableofcontents
\end{frame}

%\subsection{Announcements}
%\begin{frame}
%  \frametitle{Announcements}
%  
%\end{frame}

\section{Maximum and Minimum Values}

\begin{frame}
  \frametitle{Introduction to Applications of Differentiation}
  \begin{itemize}[<+->]
  \item The big idea of chapter 2 (Derivatives) was to obtain information
    about derivatives $df/dx$ when we are given a function $f(x)$.
  \item The answers in chapter 2 were almost all of the form $dy/dx=$
    something or $dy/dt=$ something.
  \item The big idea of chapter 3 (Application of Differentiation) is to
    obtain information about $f(x)$ from the derivative $df/dx$.
  \item The major classes of applications we will study in this chapter
    are optimization, curve sketching, and approximation.
  \item In section 3.1 we will study the simplest type of optimization,
    finding the maximum and minumum values of a continuous function on
    a closed interval (an interval containing its endpoints).
  \end{itemize}
\end{frame}

\subsection{Absolute and Local Maxima and Minima}

\begin{frame}
  \frametitle{Absolute Maxima and Minima}
  \begin{itemize}[<+->]
  \item Typically we are interested in the questions ``What is the best
    we can do?'' or ``What is the most we can get from a situation?''
  \item In the language of mathematics, if we have a function $f(x)$,
    we are interested in finding a number $c$ such that $f(c)$ is the 
    biggest number that $f(x)$ takes.
  \item We can write that as $f(c)\ge f(x)$ for all $x$ in the
    domain of $f$.
  \item \textbf{Definition:}  A function $f$ has an \textbf{absolute
    maximum} or \textbf{global maximum} at $c$ if $f(c)\ge f(x)$ for 
    all $x$ in $D$, the domain of $f$.
  \item We can make a similar definition for Absolute minimum values
    by changing the direction of the inequality.
  \item \textbf{Definition:}  A function $f$ has an \textbf{absolute
    minimum} or \textbf{global minimum} at $c$ if $f(c)\le f(x)$ for
    all $x$ in $D$, the domain of $f$.
  \item The maximum and minimum values of $f$ (i.e., $f(c)$ in the above,
    not $c$) are called the \textbf{extreme values} of $f$.
  \end{itemize}
\end{frame}

%\begin{frame}
%  \frametitle{Illustration of Absolute Extrema}
%  EJD : diagrams
%\end{frame}

\begin{frame}
  \frametitle{Local Maxima and Minima}
  \begin{itemize}[<+->]
  \item Imagine you are standing on a hill.  You are standing higher than
    anything immediately around you.  You can't go any higher by moving
    in any direction.
    But you are not standing on the highest point on earth (Mount 
    Everest).
  \item In that example, the peak of Mount Everest is the absolute maximum,
    while your hill is a local maximum.  Local maxima and minima are useful
    and interesting in their own right.
  \item \textbf{Definition:} A function $f$ has a \textbf{local maximum}
    or \textbf{relative maximum} at $c$ if $f(c)\ge f(x)$ when $x$ is near
    $c$.
  \item \textbf{Definition:} A function $f$ has a \textbf{local minimum}
    or \textbf{relative minimum} at $c$ if $f(c)\le f(x)$ when $x$ is
    near $c$.
  \item To be a little more precise, ``$x$ is near $c$'' means ``in some
    open interval containing $c$''.  An open interval is an interval which
    does not include its endpoints.
  \end{itemize}
\end{frame}

%\begin{frame}
%  \frametitle{Illustration of Local Extrema}
%  EJD : diagrams
%\end{frame}


\subsection{The Extreme Value Theorem}

\begin{frame}
  \frametitle{Existence of Absolute Maxima and Minima}
  \begin{itemize}[<+->]
  \item One of the first questions we should ask is
    ``when is a function guaranteed to have an
    absolute maximum and minimum value?''
  \item We could waste a lot of time looking for absolute maxima and minima
    if they don't exist.
  \item Fortunately, in many common situations we can guarantee the
    existence of maxima and minima.
  \item The situation we will concentrate on in this section is when $f$
    is a continuous function defined on a closed domain $D=[a,b]$.
  \item \textbf{Extreme Value Theorem:} If $f$ is continuous on a closed
    interval $[a,b]$ then $f$ attains an absolute maximum value $f(c)$
    and an absolute minumum value $f(d)$ for some numbers $c$ and $d$ 
    in $[a,b]$.
  \item The Extreme Value Theorem is similar to the Intermediate Value
    Theorem in chapter 1.  Both are hard to prove.  The idea is to use
    a successive approximations process.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Location of Extreme Values}
  \begin{columns}
  \column{0.65\textwidth}
  \begin{itemize}[<+->]
  \item Note that a maximum can occur at a point $c$ between the 
    endpoints $a$ and $b$ of the interval, or it can occur at an endpoint
    $a$ or $b$.
  \item Similarly, a minimum can occur between $a$ and $b$, or at $a$, or
    at $b$.
  \item There may also be multiple numbers $c$ at which the function attains
    its maximum.  The Extreme Value Theorem guarantees one but there may
    be more.
  \end{itemize}
  \column{0.35\textwidth}
  % EJD : diagrams
  \end{columns}
\end{frame}

\beginf{frame}
  \frametitle{Necessary Conditions for the Extreme Value Theorem}
  \begin{columns}
  \column{0.65\textwidth}
  \begin{itemize}[<+->]
  \item There are two conditions that must be met before we can
    apply the extreme value theorem.
  \item First, $f$ must be continuous.  If $f$ is not continuous there
    is no guarantee that there will be an extreme value.
  \item Second, $f$ must be defined on a closed interval.  If $f$ is
    defined on an open or half-open interval there is no guarantee that
    there will be an extreme value.
  \end{itemize}
  \column{0.35\textwidth}
  % EJD : diagrams
  \end{columns}
\end{frame}


\subsection{Fermat's Theorem and Critical Numbers}

\begin{frame}
  \frametitle{Fermat's Theorem}
  \begin{itemize}[<+->]
  \item We want to find local extrema of a given function $f$.
  \item Fortunately, the derivative $f'$ will help us find extrema.
  \item The idea is that if we are at a local maximum, we can't go any higher.
  \item If $f'(c)>0$, then $f(c+dx)\approx f(c)+f'(c)dx >f(c)$ for $dx>0$;
    that means that if $f'(c)>0$, $f$ can't have a maximum at $c$.
  \item Similarly, if $f'(c)<0$, then $f(c+dx)\approx f(c)+f'(c)dx >f(c)$
    for $dx<0$; that means that if $f'(c)<0$, $f$ can't have a maximum at
    $c$ either.
  \item Similar reasoning applies for minima.
  \item \textbf{Fermat's Theorem:} If $f$ has a local maximum or minimum
    at $c$, and $f'(c)$ exists, then $f'(c)=0$.
  \item For those of you who are interested, a rigorous proof of Fermat's
    Theorem is in the textbook.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Critical Numbers}
  \begin{columns}
  \column{0.75\textwidth}
  \begin{itemize}[<+->]
  \item Unfortunately, the analysis of the local maxima and minima of
    a function is not so simple if $f$ is not differentiable everywhere.
  \item We introduce a new definition to help us single out all the points
    of interest.
  \item \textbf{Definition:} A \textbf{critical number} of a function $f$
    is a number $c$ such that either $f'(c)=0$ or $f'(c)$ does not exist.
  \item With that new defintion, Fermat's Theorem can be re-phrased as
    follows:
  \item \textbf{Fermat's Theorem:} If $f$ has a local maximum or minimum
    at $c$, then $c$ is a critical number of $f$.
  \end{itemize}
  \column{0.25\textwidth}
  % EJD : diagram
  \end{columns}
\end{frame}


\subsection{The Closed Interval Method}

\begin{frame}
  \frametitle{The Closed Interval Method for Optimization}
  \begin{itemize}[<+->]
  \item We now turn to the problem of finding the absolute maximum and
    minimum values of a function $f$.
  \item For the time being,
    the only situation in which we are guaranteed absolute maximum and
    minimum values is the context of the Extreme Value Theorem,
    we concentrate on continuous functions $f$ defined on a closed interval
    $[a,b]$.
  \item A process which is guaranteed to find the absolute maximum and
    minimum values of such an $f$ is as follows:
    \begin{enumerate}
    \item Find the critical numbers $c$ of $f$ in the open interval $(a,b)$
    \item Find the values of $f$ at each of those critical numbers.
    \item Find the values of $f$ at each of the endpoints $a$ and $b$.
    \item The largest of the values from the previous two steps is the
      absolute maximum value; the smallest of the values is the absolute
      minimum value.
    \end{enumerate}
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{The Closed Interval Theorem in Action}
  \begin{itemize}[<+->]
  \item For example, let's try find the absolute extrema of the 
    function $f(x)=x^4-2x^2+3$ on the interval $[-2,3]$.
    \begin{enumerate}[<+->]
    \item We find the critical numbers of $f$ by noting where $f'(x)=4x^3-4x$
      exists (everywhere) and solving the equation $f'(c)=0$ i.e., 
      $4c(c-1)(c+1)=0$
      which gives critical numbers $c=0$, $c=-1$, $c=1$.
    \item We evaluate $f$ at each of those critical numbers:
      $f(0)=3$, $f(-1)=2$, $f(1)=2$.
    \item We evaluate $f$ at the endpoints of the domain: $f(-2)=11$, $f(3)
      = 66$.
    \item The largest of the above values is $66$, so $f$ has a maximum value
      of $66$ at the endpoint $b=3$.  The smallest of the above values is
      $2$, so $f$ has a minimum value of $2$ at both interior points $c=-1$
      and $c=1$.
    \end{enumerate}
  \end{itemize}
\end{frame}


\section{Examples and Exercises}

\begin{frame}
  \frametitle{Examples}
  \begin{enumerate}
  \item Find the critical numbers of the given functions.
    \begin{enumerate}
    \item $\ds f(x)=x^3+3x^2-24x$
    \item $\ds s(t)=3t^4+4t^3-6t^2$
    \item $\ds g(y)=\frac{y-1}{y^2-y+1}$
    \end{enumerate}
  \item Find the local and absolute extreme values of the
    function on the given interval.
    \begin{enumerate}
    \item $f(x)=x\sqrt{1-x}$, $[-1,1]$
    \item $f(x)=(x^2+2x)^3$, $[-2,1]$
    \item $f(x)=\sin x + \cos^2 x$, $[0,\pi]$
    \end{enumerate}
  \item Between $0^\circ$ C and $30^\circ$ C, the volume $V$ (in cm$^3$) of
    1 kg of water at temperature $T$ is given approximately by
    \begin{align*}
      V = 999.87 - 0.06426 T + 0.0085043 T^2 - 0.0000679 T^3
    \end{align*}
    Find the temperature at which water has its maximum density.
  \end{enumerate} 
\end{frame}

\begin{frame}
  \frametitle{Exercises}
  Now you should work on Problem Set~3.1.  After you have finished it,
  you should try the following additional exercises from Section~3.1:
  \begin{itemize}
  \item[3.1] 
    C-level: 1--42, 45--56; 
    B-level: 57--65, 67--68; 
    A-level: 43--44, 69--70, 72
  \end{itemize}
\end{frame}


\end{document}

