\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{mathptmx}
\usepackage[aux]{rerunfilecheck}

\newcommand{\ds}{\displaystyle}

\input{../common.tex}

\title{\commonPSTitleZeroTwoFive}
\author{\commonAuthor}
\date{\commonDateZeroTwoFive}

\begin{document}
\maketitle
\thispagestyle{empty}

\noindent
The following problems based on Section~2.5 of the textbook will help
you study.  \emph{You do not need to hand in solutions to these
  problems.}
\begin{enumerate}
\item (Based on 2.5.7--46) %1
  Find the derivatives of the following functions.
  \begin{multicols}{4}
  \begin{enumerate}
  \item $\ds \vphantom{\sqrt{\frac{t}{t^2}}} g(x)=(5x+x^3)^7$
 %\item $\ds \vphantom{\sqrt{\frac{t}{t^2}}} H(t) = t^2 e^{kt}$
  \item $\ds \vphantom{\sqrt{\frac{t}{t^2}}} H(t) = t^2 \cos kt$
  \item $\ds \vphantom{\sqrt{\frac{t}{t^2}}} (1+2z)^{10}(3-2z)^8$
  \item $\ds \vphantom{\sqrt{\frac{t}{t^2}}} W(t)=\sqrt{\frac{t}{t^2+4}}$
  \end{enumerate}
  \end{multicols}
\item (Based on 2.5.51--54) %2
  Find an equation of the tangent line to the curve $y=x\sin (3x-\pi)$
  at the point $(\pi/2,\pi/2)$ on the curve.  Also find an equation of
  the normal line to that curve at the given point.
\item (Based on 2.5.47--50) %3
  Find the second derivative of the function $y=x^2\cos 3x$
%\item %4 Find all points on the graph of the curve $y=xe^{-x}$ where the
%  graph is horizontal (i.e., where it has a horizontal tangent).
%  FIXME : variation on 2\sin x + \sin^2 x question in textbook; \cos?
\item (Based on 2.5.59) %5
  Find all points on the graph of the curve $y=2\sin x + \sin^2 x$
  where the graph is horizontal (i.e., where it has a horizontal
  tangent).
\item (Based on 2.5.61--62) %6
  If $F(x)=f(g(x))$ where $f(-1)=3$, $f'(-1)=4$, $g(2)=-1$, and
  $g'(2)=5$, find $F'(2)$
% FIXME : graph question
\item (Based on 2.5.70) %7
  If $f(x)=xg(x^2)$, find $f''(x)$ in terms of $g$, $g'$, and $g''$.
% \item %8
%  Show that the function
%  \begin{equation*}
%    y = A e^{2x} + Bxe^{2x}
%  \end{equation*}
%  satisfies the equation
%  \begin{equation*}
%    y'' - 4y' + 4y = 0
%  \end{equation*}
\item (Based on 2.4.53) %9
  Show that the function
  \begin{equation*}
    y = A \sin 2t + B \cos 2t
  \end{equation*}
  satisfies the equation
  \begin{equation*}
    y'' + 4y = 0
  \end{equation*}
\item (Based on 2.5.73--74) %10
  Find the 23rd derivative of $y=\cos 2x$.
\item (Based on 2.5.78) %11
  The number of hours of daylight in Regina on day $t$ of the year
  (counting from January 1 which is day 1) is given (approximately) by
  the formula
  \begin{equation*}
    L(t) = 12 + 4.25 \sin \left[ \frac{2\pi}{365} (t-80) \right]
  \end{equation*}
  At what rate is the number of hours of daylight changing on April 1,
  on June 21, and on December 1?  (Assume that the current year has
  365 days.)
\item (Based on 2.5.87) %12
  Recall that $\cos \theta$ is the cosine of an angle as a function of
  the measure $\theta$ of the angle in radians.  Let $\cos^{\circ} t$
  be the cosine of an angle as a function of the measure $t$ of the
  angle in degrees.
  \begin{enumerate}
  \item What is the relationship between the measure $\theta$ of an
    angle in radians and the measure $t$ of the same angle in degrees? 
  \item Write $\cos^{\circ}$ in terms of $\cos$
  \item Find $\ds \frac{d}{dt} \cos^{\circ} t$.  (Note that the answer
    is somewhat more complicated than $\ds \frac{d}{d\theta} \cos
    \theta$.  That is one of the reasons why we use radian measure
    rather than degree measure for angles in calculus.)
  \end{enumerate}
\end{enumerate}

\noindent
You may find the following additional exercises from Section~2.5
helpful.
\begin{itemize}
\item[2.5] 
  C-level: 1--6, 7--46, 47--50, 51--54, 55--57, 59--60, 61--64,
  67--68, 69--72 \\ 
  B-level: 58, 65--66, 73--74, 75--76, 77--80 \\
  A-level: 83--90
\end{itemize}




\end{document}
