\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{mathptmx}
\usepackage[aux]{rerunfilecheck}

\newcommand{\ds}{\displaystyle}

\input{../common.tex}

\title{\commonPSTitleZeroFiveOne}
\author{\commonAuthor}
\date{\commonDateZeroFiveOne}

\begin{document}
\maketitle
\thispagestyle{empty}

\noindent
The following problems based on Section~5.1 of the textbook will help
you study.  \emph{You do not need to hand in solutions to these
  problems.}
\begin{enumerate}
\item (Based on 5.1.5--10) %1
  Sketch the region enclosed by the given curves.  Draw a typical
  approximating rectangle and label its height and width.  Then find
  the area of the region.
  \begin{multicols}{4}
  \begin{enumerate}
  \item $y=x^2-2x$, \\ $y=x+4$
  \item $y=1+\sqrt{x}$, \\ $y=(3+x)/3$
  \item $y=x^2$, \\ $y=4x-x^2$
  \item $y=\cos x$, \\ $y=2-\cos x$, \\ $0\le x\le 2\pi$
  \end{enumerate}
  \end{multicols}
\item (Based on 5.1.13--28) %2
  Sketch the region enclosed by the given curves.  Decide whether to
  integrate with respect to $x$ or $y$.  Draw a typical approximating
  rectangle and label its height and width.  Then find the area of the
  region.
  \begin{multicols}{4}
  \begin{enumerate}
  \item $4x+y^2=12$, \\ $x=y$
  \item $y=\sin(\pi x/2)$, \\ $y=x$
  \item $y=\cos x$, \\ $y=1-\cos x$, \\ $0\le x\le \pi$
  \item $y=|x|$, \\ $y=x^2-2$
  \end{enumerate}
  \end{multicols}
\item (Based on 5.1.35--36) %3
  Evaluate the integral $\ds\int_0^4 \left| \sqrt{x+2}-x\right| \; dx$
  and interpret it as the area of a region.  Sketch the region.
\item (Based on 5.1.50) %4
  If the birth rate of a population is $b(t)=2200 + 52.3t + 0.74t^2$
  people per year and the death rate is $d(t)=1460+28.8t$ people per
  year, find the area between these two curves for $0\le t\le 10$.
  What does this area represent?
\item (Based on 5.1.56) %5
  Find the area of the region bounded by the parabola $y=x^2$, the
  tangent line to this parabola at $(1,1)$, and the $x$-axis.
\end{enumerate}

\noindent
You may find the following additional exercises from Section~5.1
helpful.
\begin{itemize}
\item[5.1]
  C-level: 1--28, 29, 30--32; \\
  B-level: 33--38, 46--50; \\
  A-level: 53--60.
\end{itemize}

\end{document}



